---
title: "EN_RPT_FILE_ANA_BAS"
author: "M.Shafiqul Islam"
date: "Friday, March 20, 2015"
output: html_document
---
####Write a basic function to Read 
```{r}
epanetresults<-function(fileName, objSearch, SimDur, RepInterval){
  # Step 1:
  
  # This function will give node/ link results taking from EPANET *.rpt file
  #Function takes four arguments
  
  #fileName=epanet *.rpt file
  # objSearch = Node or Link for which results will be extracte
  # SimDur= Simulation duration in Hour
  # RepInterval = Report time steps
  
  
  
  
#fileName="10d10mg_res.rpt"
NorepTime=SimDur/RepInterval
conn=file(fileName,open="r")
on.exit(close(conn))
linn=readLines(conn)


totNoLines=length(linn)
for (i in 1:length(linn)){
    
  mm=grepl(objSearch, linn[i]) 

  if (mm){
      NodePosi=i
      #print(NodePosi)
      break
      } 
}

#close(conn)


hd <- read.table(fileName, header = TRUE, sep = "", skip=NodePosi+1, nrow=1, fill=TRUE)
x <- read.table(fileName, header = TRUE, sep = "", skip=NodePosi+3, nrow=NorepTime+1, fill=TRUE)

names(x)<-names(hd) # Assigns Column Names by taking table heading from table "hd"
x$Time<-c(0,1:NorepTime) # To start time from zero
return(x)
}

```
### Calling the previous function for EPANET " *.RPT" file processing
```{r}

#Step 2:
#Before running this file, you must run epanetresults.R functions
#This will give all stations results in 3d matrix
#This section takes long time to load 
#To plot results pls use epanet_sg_plpt script


stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43) 

SimDur=120
RepInterval=0.25
NorepTime=SimDur/RepInterval
no_Stn=length(stnLoc)
no_spece=4


stations = array(0, dim=c(no_Stn,NorepTime+1,no_spece))


for (ii in 1:length(stnLoc)){
  staName=paste0("Stn_",stnLoc[ii],"_P")
  
  yy<-epanetresults("rptPHFCA20d5.rpt", staName, SimDur, RepInterval)
  
  #function(fileName, objSearch, SimDur, RepInterval)
  
  
  KK<-as.matrix(yy)

  stations[ii, , ] <-KK
  
}


```


Observed Data Prepration
```{r}
library("chron")
# Time  for #35
tms35<-times(c("8:30:00","10:30:00", "12:00:00"))
dts35<-dates(c("6/23/2015", "6/23/2015","6/23/2015"))
times35<-chron(dates=dts35, times=tms35, format = c(dates = "m/d/y", times = "h:m:s"))






# Time  for #30
tms30<-times(c("9:46:00","11:12:00","12:35:00","13:45:00"))
dts30<-dates(c("6/23/2015", "6/23/2015","6/23/2015","6/23/2015"))
times30<-chron(dates=dts30, times=tms30, format = c(dates = "m/d/y", times = "h:m:s"))




# Time  for #19
tms19<-times(c("14:15:00", "14:45:00", "15:15:00", "15:45:00","16:15:00","16:45:00", "17:15:00"))
dts19<-dates(c("6/23/2015", "6/23/2015","6/23/2015","6/23/2015", "6/23/2015","6/23/2015","6/23/2015"))
times19<-chron(dates=dts19, times=tms19, format = c(dates = "m/d/y", times = "h:m:s"))



# Time  for #20
tms20<-times(c("0:55:00", "2:35:00","4:15:00"))

dts20<-dates(c("6/24/2015", "6/24/2015","6/24/2015")) # Accurate date is 6/24/2015
#dts20<-dates(c("6/23/2015", "6/23/2015","6/23/2015")) # Accurate date is 6/24/2015
times20<-chron(dates=dts20, times=tms20, format = c(dates = "m/d/y", times = "h:m:s"))



# Time  for #14

tms14<-times(c("1:47:00","3:36:00","4:48:00"))
dts14<-dates(c("6/24/2015", "6/24/2015","6/24/2015")) # Accurate date is 6/24/2015
#dts14<-dates(c("6/23/2015", "6/23/2015","6/23/2015")) # Accurate date is 6/24/2015
times14<-chron(dates=dts14, times=tms14, format = c(dates = "m/d/y", times = "h:m:s"))



# Time  for #26

tms26<-times(c("11:40:00", "12:15:00","12:48:00","15:12:00"))
dts26<-dates(c("6/24/2015", "6/24/2015","6/24/2015","6/24/2015")) # Accurate date is 6/24/2015
#dts26<-dates(c("6/23/2015", "6/23/2015","6/23/2015","6/23/2015")) # Accurate date is 6/24/2015
times26<-chron(dates=dts26, times=tms26, format = c(dates = "m/d/y", times = "h:m:s"))



# Time  for #33

tms33<-times(c("9:55:00","10:25:00","10:55:00","11:30:00","12:00:00","12:30:00","13:00:00"))
dts33<-dates(c("6/25/2015", "6/25/2015","6/25/2015","6/25/2015","6/25/2015","6/25/2015","6/25/2015")) # Accurate date is 6/24/2015
#dts33<-dates(c("6/23/2015", "6/23/2015","6/23/2015","6/23/2015","6/23/2015","6/23/2015","6/23/2015")) # Accurate date is 6/24/2015
times33<-chron(dates=dts33, times=tms33, format = c(dates = "m/d/y", times = "h:m:s"))



# Time  for #31

tms31<-times(c("19:20:00","19:50:00","20:20:00","20:50:00","21:20:00","21:50:00","22:15:00"))
dts31<-dates(c("6/25/2015", "6/25/2015","6/25/2015","6/25/2015","6/25/2015","6/25/2015","6/25/2015")) # Accurate date is 6/24/2015
#dts31<-dates(c("6/23/2015", "6/23/2015","6/23/2015","6/23/2015","6/23/2015","6/23/2015","6/23/2015")) # Accurate date is 6/24/2015
times31<-chron(dates=dts31, times=tms31, format = c(dates = "m/d/y", times = "h:m:s"))



# Time  for #43

tms43<-times(c("8:30:00","9:00:00","9:30:00", "10:00:00","10:30:00","11:00:00","11:30:00","12:00:00"))
dts43<-dates(c("6/26/2015", "6/26/2015","6/26/2015","6/26/2015","6/26/2015","6/26/2015","6/26/2015","6/26/2015")) # Accurate date is 6/24/2015
#dts43<-dates(c("6/23/2015", "6/23/2015","6/23/2015","6/23/2015","6/23/2015","6/23/2015","6/23/2015","6/23/2015")) # Accurate date is 6/24/2015
times43<-chron(dates=dts43, times=tms43, format = c(dates = "m/d/y", times = "h:m:s"))






```



  Time           cNH3      cNH2CL        cNH4


Exporting plot specific simulation results to CSV file
It gives contineous data not pont to point
For point to point data we need to go extract corresponding point whihc has been done later
```{r}
library("prospectr")
pp=3
et=481 # end time
st=97# start time
# Plot for Stn 35
#stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43)

p35<- stations[,97:et,pp][1,]
p30<- stations[,97:et,pp][2,]
p19<- stations[,97:et,pp][3,]
p20<- stations[,97:et,pp][4,]
p14<- stations[,97:et,pp][5,]
p26<- stations[,97:et,pp][6,]
p33<- stations[,97:et,pp][7,]
p31<- stations[,97:et,pp][8,]
p43<- stations[,97:et,pp][9,]

write.csv(cbind(p35, p30,p19, p20,p14, p26,p33, p31,p43), file="Atm20_TRC.csv") # Change file name based on which parametes are exporting


```
NO need to run previous section if no new rpt file is tehre


Reading data from saved file
```{r}


#Reading Observed data
#Time need to process which have been proceed in the next chunk

cnames<-c("Time", "TRC", "FC", "Tem", "pH", "NH3", "NH4", "CON","FDOM", "TDS", "ORP")

ob35<-read.csv("PHFC_Observed35.csv", skip=2, nrow=3)
ob30<-read.csv("PHFC_Observed30.csv", skip=2, nrow=4)
ob19<-read.csv("PHFC_Observed19.csv", skip=2, nrow=7)
ob20<-read.csv("PHFC_Observed20.csv", skip=2, nrow=3)
ob14<-read.csv("PHFC_Observed14.csv", skip=2, nrow=3)
ob26<-read.csv("PHFC_Observed26.csv", skip=2, nrow=4)
ob33<-read.csv("PHFC_Observed33.csv", skip=2, nrow=7)
ob31<-read.csv("PHFC_Observed31.csv", skip=2, nrow=7)
ob43<-read.csv("PHFC_Observed43.csv", skip=2, nrow=8)
pub<-read.csv("PUB.csv", skip=0, nrow=10)

names(ob35)<-cnames
names(ob30)<-cnames
names(ob19)<-cnames
names(ob20)<-cnames
names(ob14)<-cnames
names(ob26)<-cnames
names(ob33)<-cnames
names(ob31)<-cnames
names(ob43)<-cnames

```





PLotting Simulation and observation data (Specific time duration)
```{r}

# Reading stored results from saved CSV file. No need to run long search file
#atm4<-read.csv("Atm34_NH4.csv")
atm3<-read.csv("Atm20_TRC.csv")


par(mfrow=c(2,1))
param1="TRC(mg/L)" # Related titles
obp="TRC"
yul=1.7 # Y upper limit plot

library("chron")
# Time 23 june morning
t1 <- chron("6/23/2015", "00:00:00")
t2 <- chron("6/26/2015", "16:00:00")
tt230615_1 <- seq(t1, t2, by = times("00:15:00"))
#stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43) 



# Plot for Stn 35
plot(tt230615_1,atm3$p35,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_35_P (Boon Keng Road)"),xlab="Time", ylab=param1)

#lines(tt230615_1,atm4$p35,type='l', ylim=c(0,yul), ylab=param1, col="blue")

lines(times35,eval(parse(text=paste0('ob35$',obp))), col="red", type='p')

#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))

legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))


# Plot for Stn 30

plot(tt230615_1,atm3$p30,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_30_P (Beach Rd) "), xlab="Time", ylab=param1)
#lines(tt230615_1,atm4$p30,type='l', ylim=c(0,yul), ylab=param1, col="blue")
lines(times30,eval(parse(text=paste0('ob30$',obp))), col="red", type='p')
#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))
legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))

```

# Time 23 june Afternoon
t1 <- chron("6/23/2015", "00:00:00")
t2 <- chron("6/26/2015", "16:00:00")
tt230615_2 <- seq(t1, t2, by = times("00:15:00"))
#stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43)


# Plot for Stn 19


plot(tt230615_2,atm3$p19,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_19_P (Victoria Rd) "), xlab="Time", ylab=param1)
#lines(tt230615_2,atm4$p19,type='l', ylim=c(0,yul), ylab=param1, col="blue")
lines(times19,eval(parse(text=paste0('ob19$',obp))), col="red", type='p')
#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))
legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))

# Time 24 june Early Morning
t1 <- chron("6/23/2015", "00:00:00")
t2 <- chron("6/26/2015", "16:00:00")
tt240615_1 <- seq(t1, t2, by = times("00:15:00"))
#stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43)




# Plot for Stn 20


plot(tt240615_1,atm3$p20,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_20_P (Handy Rd)"), xlab="Time", ylab=param1)
#lines(tt240615_1,atm4$p20,type='l', ylim=c(0,yul), ylab=param1, col="blue")
lines(times20,eval(parse(text=paste0('ob20$',obp))), col="red", type='p')
#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))
legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))

# Plot for Stn 14


plot(tt240615_1,atm3$p14,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_14_P (Hill St) "), xlab="Time", ylab=param1)
#lines(tt240615_1,atm4$p14,type='l', ylim=c(0,yul), ylab=param1, col="blue")
lines(times14,eval(parse(text=paste0('ob14$',obp))), col="red", type='p')
#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))
legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))


# Time 24 june  Morning & Afternoon
t1 <- chron("6/23/2015", "00:00:00")
t2 <- chron("6/26/2015", "16:00:00")
tt240615_2 <- seq(t1, t2, by = times("00:15:00"))
#stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43)


# Plot for Stn 26


plot(tt240615_2,atm3$p26,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_26_P (Keppel Rd) "), xlab="Time", ylab=param1)
#lines(tt240615_2,atm4$p26,type='l', ylim=c(0,yul), ylab=param1, col="blue")
lines(times26,eval(parse(text=paste0('ob26$',obp))), col="red", type='p')
#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))
legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))



# Time 25 june  Morning 
t1 <- chron("6/23/2015", "00:00:00")
t2 <- chron("6/26/2015", "16:00:00")
tt250615_1 <- seq(t1, t2, by = times("00:15:00"))
#stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43)

# Plot for Stn 33


plot(tt250615_1,atm3$p33,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_33_P (Cove Dr) "), xlab="Time", ylab=param1)
#lines(tt250615_1,atm4$p33,type='l', ylim=c(0,yul), ylab=param1, col="blue")
lines(times33,eval(parse(text=paste0('ob33$',obp))), col="red", type='p')
#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))
legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))





# Time 25 june  Afternoon 
t1 <- chron("6/23/2015", "00:00:00")
t2 <- chron("6/26/2015", "16:00:00")
tt250615_2 <- seq(t1, t2, by = times("00:15:00"))
#stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43)


# Plot for Stn 31


plot(tt250615_2,atm3$p31,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_31_P (Santosa Gateway) "), xlab="Time", ylab=param1)
#lines(tt250615_2,atm4$p31,type='l', ylim=c(0,yul), ylab=param1, col="blue")
lines(times31,eval(parse(text=paste0('ob31$',obp))), col="red", type='p')
#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))
legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))
```

```{r}

# Time 26 june  Morning 
t1 <- chron("6/23/2015", "00:00:00")
t2 <- chron("6/26/2015", "16:00:00")
tt260615_1 <- seq(t1, t2, by = times("00:15:00"))
#stnLoc<-c(35,30,19, 20, 14, 26, 33, 31, 43)




# Plot for Stn 43
#NH2CL43<- stations[,st:et,pp][9,]

plot(tt260615_1,atm3$p43,type='l', ylim=c(0,yul), main=paste(param1, "at Stn_43_P (Bayfront Ave)"), xlab="Time", ylab=param1)
#lines(tt260615_1,atm4$p43,type='l', ylim=c(0,yul), ylab=param1, col="blue")
lines(times43,eval(parse(text=paste0('ob43$',obp))), col="red", type='p')
#legend("bottomright", pch=c(1,NA, NA), lty=c(NA,1,1), col=c("red","black","blue"), legend=c("Observed","Simulated A3", "Simulated A4"))

legend("bottomright", pch=c(1,NA), lty=c(NA,1), col=c("red","black"), legend=c("Observed","Simulated"))
```

```{r}

# Production graph


par(mfrow=c(1,1))

obp="TRC"
yul=2.0

plot(tt240615_1,atm3$p14,type='l', ylim=c(0,yul), xlab="Time", ylab=param1, col='red', main=paste("Comparison of Observed and Simulated", obp, "(mg/L)"))
points(times14,eval(parse(text=paste0('ob14$',obp))), col="red", pch=0)

lines(tt230615_2,atm3$p19,type='l', col="green")
points(times19,eval(parse(text=paste0('ob19$',obp))), col="green", pch=1)

lines(tt240615_1,atm3$p20,type='l', col="azure3")
points(times20,eval(parse(text=paste0('ob20$',obp))), col="azure3", pch=2)

lines(tt240615_2,atm3$p26,type='l', col="blue")
points(times26,eval(parse(text=paste0('ob26$',obp))), col="blue", pch=3)


lines(tt230615_1,atm3$p30,type='l', col="purple")
points(times30,eval(parse(text=paste0('ob30$',obp))), col="purple", pch=4)

lines(tt250615_2,atm3$p31,type='l', col="orange")
points(times31,eval(parse(text=paste0('ob31$',obp))), col="orange", pch=5)

lines(tt250615_1,atm3$p33,type='l', col="black")
points(times33,eval(parse(text=paste0('ob33$',obp))), col="black", pch=6)

lines(tt230615_1,atm3$p35,type='l', col="cyan")
points(times35,eval(parse(text=paste0('ob35$',obp))), col="cyan", pch=7)

lines(tt260615_1,atm3$p43,type='l', col="brown4")
points(times43,eval(parse(text=paste0('ob43$',obp))), col="brown4", pch=8)



legend("bottomright", pch=c(0, 1,2,3,4,5,6,7,8), col=c('red','green', 'azure3','blue', 'purple','orange', 'black', 'cyan', 'brown4'), legend=c('Hill St', 'Victoria Rd', 'Handy Rd', 'Keppel Rd', 'Beach Rd', 'Santosa Gateway','Cove Dr', 'Boon Keng Road','Bayfront Ave'))

```




Plotting Point to point

```{r}
#Reults with vareibale (optimized) kdoc
dp<-read.csv("C:\\Users\\User\\Desktop\\Host-Guest\\DataPrepEXLmod.csv", skip=0, nrow=46)

# Results with all high kDOC
#dp<-read.csv("C:\\Users\\User\\Desktop\\Host-Guest\\Data Prep For PEST and Analysis_v2.csv", skip=0, nrow=46)


aNH3=dp$NH3.1 # all Station NH3
aTRC=dp$NH2Cl.1 # all Station NH3
aNH4=dp$NH4.1 # all Station NH3

sim14TRC=aTRC[1:3]
sim19TRC=aTRC[4:10]
sim20TRC=aTRC[11:13]
sim26TRC=aTRC[14:17]
sim30TRC=aTRC[18:21]
sim31TRC=aTRC[22:28]
sim33TRC=aTRC[29:35]
sim35TRC=aTRC[36:38]
sim43TRC=aTRC[39:46]

sim14NH3=aNH3[1:3]
sim19NH3=aNH3[4:10]
sim20NH3=aNH3[11:13]
sim26NH3=aNH3[14:17]
sim30NH3=aNH3[18:21]
sim31NH3=aNH3[22:28]
sim33NH3=aNH3[29:35]
sim35NH3=aNH3[36:38]
sim43NH3=aNH3[39:46]

sim14NH4=aNH4[1:3]
sim19NH4=aNH4[4:10]
sim20NH4=aNH4[11:13]
sim26NH4=aNH4[14:17]
sim30NH4=aNH4[18:21]
sim31NH4=aNH4[22:28]
sim33NH4=aNH4[29:35]
sim35NH4=aNH4[36:38]
sim43NH4=aNH4[39:46]



```
Plotting
```{r}

par(mfrow=c(1,1))
obp="TRC"
par='NH2CL'

if (obp=="TRC") {
  xul=2
  yul=2
} else if (obp=="NH3") {
  xul=0.1
  yul=0.1
}else if (obp=="NH4") {
  xul=1.2
  yul=1.2
} else{
  break
}



nd=14
plot(eval(parse(text=paste0('sim',nd,obp))), eval(parse(text=paste0('ob',nd,'$',obp))),pch=0, xlim=c(0,xul), ylim=c(0,yul), main=paste("Comparison of Observed and Simulated", par, "(mg/L)"), xlab=paste("Simulated",par,"(mg/L)"), ylab=paste("Observed",par,"(mg/L)"), col='red')

ndd=c(19, 20, 26, 30, 31,33, 35,43)
cl=c('green', 'azure3','blue', 'purple','orange', 'black', 'cyan', 'brown4')

#points(eval(parse(text=paste0('sim',nd,obp))), eval(parse(text=paste0('ob',nd,'$',obp))),type='p', xlim=c(0,xul), ylim=c(0,yul), col=cl[1])


# Plotting all the remaining node data
for (i in 1:length(ndd) ) {
  nd=ndd[i]
  points(eval(parse(text=paste0('sim',nd,obp))), eval(parse(text=paste0('ob',nd,'$',obp))),pch=i, xlim=c(0,xul), ylim=c(0,yul), col=cl[i])

}

# Plotting st line
a=c(0, xul*1.1)
b=c(0, yul*1.1)

lines(a,b,type='l', col="purple")



legend("bottomright", pch=c(0, 1,2,3,4,5,6,7,8), col=c('red','green', 'azure3','blue', 'purple','orange', 'black', 'cyan', 'brown4'), legend=c('Hill St', 'Victoria Rd', 'Handy Rd', 'Keppel Rd', 'Beach Rd', 'Santosa Gateway','Cove Dr', 'Boon Keng Road','Bayfront Ave'))







      
```













Bar plot
```{r}
 mydata <- data.frame(Barplot1=rbinom(5,16,0.6), Barplot2=rbinom(5,16,0.25),
                     Barplot3=rbinom(5,5,0.25), Barplot4=rbinom(5,16,0.7))
barplot(as.matrix(mydata), main="Interesting", ylab="Total", beside=TRUE, 
        col=terrain.colors(5))
legend(13, 12, c("Label1","Label2","Label3","Label4","Label5"), cex=0.6, 
       fill=terrain.colors(5))

```





