---
title: "Online Water Quality Data Analysis"
author: "M.Shafiqul Islam"
date: "Tuesday, June 10, 2015"
output: pdf_document
---
About Data:
-This file select the good quality data based on qualitivive ranking

#### Important Notes:
- remove "2" from "Marina Blvd.2  (Stn 27) (Conductivity:uS/cm)" column
-This file has an extra station "station 44" which is not available in "Condunctivity file"

```{r}
library("ggplot2")
library("prospectr")
# Read CSV file
  fileCON="Dec14-Jan15 - PHFC CTY (30mins)M.csv" # This file has been modified by adding two extra blank columns to match dimention of ORP and pH data
  myDataCON<-read.table(fileCON, header= TRUE, sep=",") # Full data

  fileORP="Dec14-Jan15 - PHFC ORP (30mins).csv"
  myDataORP<-read.table(fileORP, header= TRUE, sep=",") # Full data


  filePH="Dec14-Jan15 - PHFC PH (30mins).csv"
  myDataPH<-read.table(filePH, header= TRUE, sep=",") # Full data

  fileTUR="Oct 14 - PHFC TURBFNU (30mins).csv"
  myDataTUR<-read.table(fileTUR, header= TRUE, sep=",") # Fudll data


# Extract names of the variable other than Time
  cnames<-names(myDataORP)
# declaring variable
  staLoc= rep(NA, 19) 
  staNo= rep(NA, 19)
  staNu= rep(NA, 19)

# Renaming column Based on the station
  for (i in 1:19){
     staLoc[i]<-cnames[2*i]
     cln<-unique(na.omit(as.numeric(unlist(strsplit(unlist(staLoc[i]), "[^0-9]+"))))) # Only extracting numbers
     staNu[i]=cln # just Station No
     staNo[i]=paste0("Stn_",cln,"_P")
     cnames[2*i]<-staNo[i]
  }
 names(myDataCON)<-cnames 
 names(myDataORP)<-cnames
 names(myDataPH)<-cnames
 names(myDataTUR)<-cnames 



# Extracting station values considering time steps and time are same

#Conductivity
sCON35<-myDataCON$Stn_35_P
sCON25<-myDataCON$Stn_25_P
sCON30<-myDataCON$Stn_30_P
sCON20<-myDataCON$Stn_20_P
sCON19<-myDataCON$Stn_19_P
sCON11<-myDataCON$Stn_11_P
sCON22<-myDataCON$Stn_22_P
sCON17<-myDataCON$Stn_17_P
sCON29<-myDataCON$Stn_29_P
sCON14<-myDataCON$Stn_14_P
sCON36<-myDataCON$Stn_36_P
sCON43<-myDataCON$Stn_43_P
sCON12<-myDataCON$Stn_12_P
sCON27<-myDataCON$Stn_27_P
sCON44<-myDataCON$Stn_44_P # It is blanck as it has been added to match dim of other spreadsheet
sCON26<-myDataCON$Stn_26_P
sCON31<-myDataCON$Stn_31_P
sCON33<-myDataCON$Stn_33_P
sCON49<-myDataCON$Stn_49_P




#ORP

sORP35<-myDataORP$Stn_35_P
sORP25<-myDataORP$Stn_25_P
sORP30<-myDataORP$Stn_30_P
sORP20<-myDataORP$Stn_20_P
sORP19<-myDataORP$Stn_19_P
sORP11<-myDataORP$Stn_11_P
sORP22<-myDataORP$Stn_22_P
sORP17<-myDataORP$Stn_17_P
sORP29<-myDataORP$Stn_29_P
sORP14<-myDataORP$Stn_14_P
sORP36<-myDataORP$Stn_36_P
sORP43<-myDataORP$Stn_43_P
sORP12<-myDataORP$Stn_12_P
sORP27<-myDataORP$Stn_27_P
sORP44<-myDataORP$Stn_44_P
sORP26<-myDataORP$Stn_26_P
sORP31<-myDataORP$Stn_31_P
sORP33<-myDataORP$Stn_33_P
sORP49<-myDataORP$Stn_49_P


#pH
sPH35<-myDataPH$Stn_35_P
sPH25<-myDataPH$Stn_25_P
sPH30<-myDataPH$Stn_30_P
sPH20<-myDataPH$Stn_20_P
sPH19<-myDataPH$Stn_19_P
sPH11<-myDataPH$Stn_11_P
sPH22<-myDataPH$Stn_22_P
sPH17<-myDataPH$Stn_17_P
sPH29<-myDataPH$Stn_29_P
sPH14<-myDataPH$Stn_14_P
sPH36<-myDataPH$Stn_36_P
sPH43<-myDataPH$Stn_43_P
sPH12<-myDataPH$Stn_12_P
sPH27<-myDataPH$Stn_27_P
sPH44<-myDataPH$Stn_44_P
sPH26<-myDataPH$Stn_26_P
sPH31<-myDataPH$Stn_31_P
sPH33<-myDataPH$Stn_33_P
sPH49<-myDataPH$Stn_49_P



#Turbidity
sTUR35<-myDataTUR$Stn_35_P
sTUR25<-myDataTUR$Stn_25_P
sTUR30<-myDataTUR$Stn_30_P
sTUR20<-myDataTUR$Stn_20_P
sTUR19<-myDataTUR$Stn_19_P
sTUR11<-myDataTUR$Stn_11_P
sTUR22<-myDataTUR$Stn_22_P
sTUR17<-myDataTUR$Stn_17_P
sTUR29<-myDataTUR$Stn_29_P
sTUR14<-myDataTUR$Stn_14_P
sTUR36<-myDataTUR$Stn_36_P
sTUR43<-myDataTUR$Stn_43_P
sTUR12<-myDataTUR$Stn_12_P
sTUR27<-myDataTUR$Stn_27_P
sTUR44<-myDataTUR$Stn_44_P
sTUR26<-myDataTUR$Stn_26_P
sTUR31<-myDataTUR$Stn_31_P
sTUR33<-myDataTUR$Stn_33_P
sTUR49<-myDataTUR$Stn_49_P


dTime2<-myDataORP$Date.Time
dTime1<-as.character(dTime2)
dTime<-as.POSIXlt(dTime1,format="%m/%d/%Y %H:%M")




```
## Plotting sample data

```{r}
par(mfrow=c(1,1))
#plot(dTime, sORP35, type='n')

ylm1=c(7,9.5)


#pH
plot(dTime[1:480], sPH35[1:480], col="red", type='l', yaxt='n',  ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(dTime[1:480], sPH25[1:480], col="green", type='l',axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(dTime[1:480], sPH30[1:480], col="blue", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(dTime[1:480], sPH17[1:480], col="brown", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(dTime[1:480], sPH14[1:480], col="purple", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)

legend("bottomright", lty=c(1,1), col=c("red", "green","blue","brown","purple"), legend=c("35", "25", "30", "17", "14"))
title("PH with time in different stations")
mtext("Time ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5)







#ORP
ylm1=c(350,500)
plot(dTime[1:480], sORP35[1:480], col="red", type='l', yaxt='n',  ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(dTime[1:480], sORP25[1:480], col="green", type='l',axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(dTime[1:480], sORP30[1:480], col="blue", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(dTime[1:480], sORP17[1:480], col="brown", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(dTime[1:480], sORP14[1:480], col="purple", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)

legend("topright", lty=c(1,1), col=c("red", "green","blue","brown","purple"), legend=c("35", "25", "30", "17", "14"))
title("ORP with time in different stations")
mtext("Time ",side=1,col="black",line=2.5) 
mtext("ORP ",side=2,col="black",line=2.5)



```



```{r}
## Function for Hour wise Data Extraction

#sData=sPH25
HourWiseData<-function(sData){
  
    nData=length(sData)/48
    HourMat=array(NA, c(nData, 48))
    for (i in 1:nData){
    
      for (j in 1:48){
        HourMat[i,j]=sData[48*(i-1)+j]
      }
      
    }
    return(HourMat)
}

## End of Function for Hourwise Data Extraction

 # Hour Wise Data for PH
sPH25HourW=HourWiseData(sPH25)
sPH29HourW=HourWiseData(sPH29)
sPH30HourW=HourWiseData(sPH30)
sPH27HourW=HourWiseData(sPH27)
sPH35HourW=HourWiseData(sPH35)
sPH43HourW=HourWiseData(sPH43)
sPH33HourW=HourWiseData(sPH33)
sPH11HourW=HourWiseData(sPH11)
sPH22HourW=HourWiseData(sPH22)
sPH17HourW=HourWiseData(sPH17)
sPH31HourW=HourWiseData(sPH31)
sPH26HourW=HourWiseData(sPH26)
sPH14HourW=HourWiseData(sPH14)
sPH19HourW=HourWiseData(sPH19)
sPH12HourW=HourWiseData(sPH12)
sPH49HourW=HourWiseData(sPH49)
sPH20HourW=HourWiseData(sPH20)
sPH36HourW=HourWiseData(sPH36)



 # Hour Wise Data for COnductivity
sCON25HourW=HourWiseData(sCON25)
sCON29HourW=HourWiseData(sCON29)
sCON30HourW=HourWiseData(sCON30)
sCON27HourW=HourWiseData(sCON27)
sCON35HourW=HourWiseData(sCON35)
sCON43HourW=HourWiseData(sCON43)
sCON33HourW=HourWiseData(sCON33)
sCON11HourW=HourWiseData(sCON11)
sCON22HourW=HourWiseData(sCON22)
sCON17HourW=HourWiseData(sCON17)
sCON31HourW=HourWiseData(sCON31)
sCON26HourW=HourWiseData(sCON26)
sCON14HourW=HourWiseData(sCON14)
sCON19HourW=HourWiseData(sCON19)
sCON12HourW=HourWiseData(sCON12)
sCON49HourW=HourWiseData(sCON49)
sCON20HourW=HourWiseData(sCON20)
sCON36HourW=HourWiseData(sCON36)



 # Hour Wise Data for ORP
sORP25HourW=HourWiseData(sORP25)
sORP29HourW=HourWiseData(sORP29)
sORP30HourW=HourWiseData(sORP30)
sORP27HourW=HourWiseData(sORP27)
sORP35HourW=HourWiseData(sORP35)
sORP43HourW=HourWiseData(sORP43)
sORP33HourW=HourWiseData(sORP33)
sORP11HourW=HourWiseData(sORP11)
sORP22HourW=HourWiseData(sORP22)
sORP17HourW=HourWiseData(sORP17)
sORP31HourW=HourWiseData(sORP31)
sORP26HourW=HourWiseData(sORP26)
sORP14HourW=HourWiseData(sORP14)
sORP19HourW=HourWiseData(sORP19)
sORP12HourW=HourWiseData(sORP12)
sORP49HourW=HourWiseData(sORP49)
sORP20HourW=HourWiseData(sORP20)
sORP36HourW=HourWiseData(sORP36)


```
#### Box and Line plot
```{r}
set.seed(121)
ylimPH=c(7.5,10.5)
ylimCON=c(140, 280)
ylimORP=c(300,480)

par(mar=rep(2,4), mfrow=c(2,1))
# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36




# Box plot CON


boxplot(sCON25HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s25"); lines(1:48, apply(na.omit(sCON25HourW), 2, mean), type="l", col="red")
boxplot(sCON29HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s29"); lines(1:48, apply(na.omit(sCON29HourW), 2, mean), type="l", col="red")
boxplot(sCON30HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s30"); lines(1:48, apply(na.omit(sCON30HourW), 2, mean), type="l", col="red")

boxplot(sCON27HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s27"); lines(1:48, apply(na.omit(sCON27HourW), 2, mean), type="l", col="red")
boxplot(sCON35HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s35"); lines(1:48, apply(na.omit(sCON35HourW), 2, mean), type="l", col="red")
boxplot(sCON43HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s43"); lines(1:48, apply(na.omit(sCON43HourW), 2, mean), type="l", col="red")

boxplot(sCON33HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s33"); lines(1:48, apply(na.omit(sCON33HourW), 2, mean), type="l", col="red")
boxplot(sCON11HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s11"); lines(1:48, apply(na.omit(sCON11HourW), 2, mean), type="l", col="red")
boxplot(sCON22HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s22"); lines(1:48, apply(na.omit(sCON22HourW), 2, mean), type="l", col="red")

boxplot(sCON17HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s17"); lines(1:48, apply(na.omit(sCON17HourW), 2, mean), type="l", col="red")
boxplot(sCON31HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s31"); lines(1:48, apply(na.omit(sCON31HourW), 2, mean), type="l", col="red")
boxplot(sCON26HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s26"); lines(1:48, apply(na.omit(sCON26HourW), 2, mean), type="l", col="red")

boxplot(sCON14HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s14"); lines(1:48, apply(na.omit(sCON14HourW), 2, mean), type="l", col="red")
boxplot(sCON19HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s19"); lines(1:48, apply(na.omit(sCON19HourW), 2, mean), type="l", col="red")
boxplot(sCON12HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s12"); lines(1:48, apply(na.omit(sCON12HourW), 2, mean), type="l", col="red")

boxplot(sCON49HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s49"); lines(1:48, apply(na.omit(sCON49HourW), 2, mean), type="l", col="red")
boxplot(sCON20HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s20"); lines(1:48, apply(na.omit(sCON20HourW), 2, mean), type="l", col="red")
boxplot(sCON36HourW, ylim=ylimCON, xlab="Hours in a Day", main="CON at s36"); lines(1:48, apply(na.omit(sCON36HourW), 2, mean), type="l", col="red")









# Boxplot ORP
boxplot(sORP25HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s25"); lines(1:48, apply(na.omit(sORP25HourW), 2, mean), type="l", col="red")
boxplot(sORP29HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s29"); lines(1:48, apply(na.omit(sORP29HourW), 2, mean), type="l", col="red")
boxplot(sORP30HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s30"); lines(1:48, apply(na.omit(sORP30HourW), 2, mean), type="l", col="red")

boxplot(sORP27HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s27"); lines(1:48, apply(na.omit(sORP27HourW), 2, mean), type="l", col="red")
boxplot(sORP35HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s35"); lines(1:48, apply(na.omit(sORP35HourW), 2, mean), type="l", col="red")
boxplot(sORP43HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s43"); lines(1:48, apply(na.omit(sORP43HourW), 2, mean), type="l", col="red")

boxplot(sORP33HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s33"); lines(1:48, apply(na.omit(sORP33HourW), 2, mean), type="l", col="red")
boxplot(sORP11HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s11"); lines(1:48, apply(na.omit(sORP11HourW), 2, mean), type="l", col="red")
boxplot(sORP22HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s22"); lines(1:48, apply(na.omit(sORP22HourW), 2, mean), type="l", col="red")

boxplot(sORP17HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s17"); lines(1:48, apply(na.omit(sORP17HourW), 2, mean), type="l", col="red")
boxplot(sORP31HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s31"); lines(1:48, apply(na.omit(sORP31HourW), 2, mean), type="l", col="red")
boxplot(sORP26HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s26"); lines(1:48, apply(na.omit(sORP26HourW), 2, mean), type="l", col="red")

boxplot(sORP14HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s14"); lines(1:48, apply(na.omit(sORP14HourW), 2, mean), type="l", col="red")
boxplot(sORP19HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s19"); lines(1:48, apply(na.omit(sORP19HourW), 2, mean), type="l", col="red")
boxplot(sORP12HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s12"); lines(1:48, apply(na.omit(sORP12HourW), 2, mean), type="l", col="red")

boxplot(sORP49HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s49"); lines(1:48, apply(na.omit(sORP49HourW), 2, mean), type="l", col="red")
boxplot(sORP20HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s20"); lines(1:48, apply(na.omit(sORP20HourW), 2, mean), type="l", col="red")
boxplot(sORP36HourW, ylim=ylimORP, xlab="Hours in a Day", main="ORP at s36"); lines(1:48, apply(na.omit(sORP36HourW), 2, mean), type="l", col="red")





# Box Plot PH

boxplot(sPH25HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s25"); lines(1:48, apply(sPH25HourW, ylim=ylimPH, 2, mean), type="l", col="red")
boxplot(sPH29HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s29"); lines(1:48, apply(na.omit(sPH29HourW), 2, mean), type="l", col="red")
boxplot(sPH30HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s30"); lines(1:48, apply(na.omit(sPH30HourW), 2, mean), type="l", col="red")

boxplot(sPH27HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s27"); lines(1:48, apply(na.omit(sPH27HourW), 2, mean), type="l", col="red")
boxplot(sPH35HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s35"); lines(1:48, apply(na.omit(sPH35HourW), 2, mean), type="l", col="red")
boxplot(sPH43HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s43"); lines(1:48, apply(na.omit(sPH43HourW), 2, mean), type="l", col="red")

boxplot(sPH33HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s33"); lines(1:48, apply(na.omit(sPH33HourW), 2, mean), type="l", col="red")
boxplot(sPH11HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s11"); lines(1:48, apply(na.omit(sPH11HourW), 2, mean), type="l", col="red")
boxplot(sPH22HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s22"); lines(1:48, apply(na.omit(sPH22HourW), 2, mean), type="l", col="red")

boxplot(sPH17HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s17"); lines(1:48, apply(na.omit(sPH17HourW), 2, mean), type="l", col="red")
boxplot(sPH31HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s31"); lines(1:48, apply(na.omit(sPH31HourW), 2, mean), type="l", col="red")
boxplot(sPH26HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s26"); lines(1:48, apply(na.omit(sPH26HourW), 2, mean), type="l", col="red")

boxplot(sPH14HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s14"); lines(1:48, apply(na.omit(sPH14HourW), 2, mean), type="l", col="red")
boxplot(sPH19HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s19"); lines(1:48, apply(na.omit(sPH19HourW), 2, mean), type="l", col="red")
boxplot(sPH12HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s12"); lines(1:48, apply(na.omit(sPH12HourW), 2, mean), type="l", col="red")

boxplot(sPH49HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s49"); lines(1:48, apply(na.omit(sPH49HourW), 2, mean), type="l", col="red")
boxplot(sPH20HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s20"); lines(1:48, apply(na.omit(sPH20HourW), 2, mean), type="l", col="red")
boxplot(sPH36HourW, ylim=ylimPH, xlab="Hours in a Day", main="PH at s36"); lines(1:48, apply(na.omit(sPH36HourW), 2, mean), type="l", col="red")

```

# Make Observed data as 24 hour data
```{r}
# making average over 30 min
#ORP
sORP25HourW48=apply(na.omit(sORP25HourW), 2, mean)
sORP29HourW48=apply(na.omit(sORP29HourW), 2, mean)
sORP30HourW48=apply(na.omit(sORP30HourW), 2, mean)
sORP27HourW48=apply(na.omit(sORP27HourW), 2, mean)
sORP35HourW48=apply(na.omit(sORP35HourW), 2, mean)
sORP43HourW48=apply(na.omit(sORP43HourW), 2, mean)
sORP33HourW48=apply(na.omit(sORP33HourW), 2, mean)
sORP11HourW48=apply(na.omit(sORP11HourW), 2, mean)
sORP22HourW48=apply(na.omit(sORP22HourW), 2, mean)
sORP17HourW48=apply(na.omit(sORP17HourW), 2, mean)
sORP31HourW48=apply(na.omit(sORP31HourW), 2, mean)
sORP26HourW48=apply(na.omit(sORP25HourW), 2, mean)
sORP14HourW48=apply(na.omit(sORP14HourW), 2, mean)
sORP19HourW48=apply(na.omit(sORP19HourW), 2, mean)
sORP12HourW48=apply(na.omit(sORP12HourW), 2, mean)
sORP49HourW48=apply(na.omit(sORP49HourW), 2, mean)
sORP20HourW48=apply(na.omit(sORP20HourW), 2, mean)
sORP36HourW48=apply(na.omit(sORP36HourW), 2, mean)

#Making 1 hour average 
# DEclaring varibales
sORP25HourW24x=rep(NA, 24)
sORP29HourW24x=rep(NA, 24)
sORP30HourW24x=rep(NA, 24)
sORP27HourW24x=rep(NA, 24)
sORP35HourW24x=rep(NA, 24)
sORP43HourW24x=rep(NA, 24)
sORP33HourW24x=rep(NA, 24)
sORP11HourW24x=rep(NA, 24)
sORP22HourW24x=rep(NA, 24)
sORP17HourW24x=rep(NA, 24)
sORP31HourW24x=rep(NA, 24)
sORP26HourW24x=rep(NA, 24)
sORP14HourW24x=rep(NA, 24)
sORP19HourW24x=rep(NA, 24)
sORP12HourW24x=rep(NA, 24)
sORP49HourW24x=rep(NA, 24)
sORP20HourW24x=rep(NA, 24)
sORP36HourW24x=rep(NA, 24)

  for (i in 1:24){
    sORP25HourW24x[i]=(sORP25HourW48[2*i-1]+sORP25HourW48[2*i])*0.5
    sORP29HourW24x[i]=(sORP29HourW48[2*i-1]+sORP29HourW48[2*i])*0.5
    sORP30HourW24x[i]=(sORP30HourW48[2*i-1]+sORP30HourW48[2*i])*0.5
    sORP27HourW24x[i]=(sORP27HourW48[2*i-1]+sORP27HourW48[2*i])*0.5
    sORP35HourW24x[i]=(sORP35HourW48[2*i-1]+sORP35HourW48[2*i])*0.5
    sORP43HourW24x[i]=(sORP43HourW48[2*i-1]+sORP43HourW48[2*i])*0.5
    sORP33HourW24x[i]=(sORP33HourW48[2*i-1]+sORP33HourW48[2*i])*0.5
    sORP11HourW24x[i]=(sORP11HourW48[2*i-1]+sORP11HourW48[2*i])*0.5
    sORP22HourW24x[i]=(sORP22HourW48[2*i-1]+sORP22HourW48[2*i])*0.5
    sORP17HourW24x[i]=(sORP17HourW48[2*i-1]+sORP17HourW48[2*i])*0.5
    sORP31HourW24x[i]=(sORP31HourW48[2*i-1]+sORP31HourW48[2*i])*0.5
    sORP26HourW24x[i]=(sORP26HourW48[2*i-1]+sORP26HourW48[2*i])*0.5
    sORP14HourW24x[i]=(sORP14HourW48[2*i-1]+sORP14HourW48[2*i])*0.5
    sORP19HourW24x[i]=(sORP19HourW48[2*i-1]+sORP19HourW48[2*i])*0.5
    sORP12HourW24x[i]=(sORP12HourW48[2*i-1]+sORP12HourW48[2*i])*0.5
    sORP49HourW24x[i]=(sORP49HourW48[2*i-1]+sORP49HourW48[2*i])*0.5
    sORP20HourW24x[i]=(sORP20HourW48[2*i-1]+sORP20HourW48[2*i])*0.5
    sORP36HourW24x[i]=(sORP36HourW48[2*i-1]+sORP36HourW48[2*i])*0.5

  }
 

#PH

sPH25HourW48=apply(na.omit(sPH25HourW), 2, mean)
sPH29HourW48=apply(na.omit(sPH29HourW), 2, mean)
sPH30HourW48=apply(na.omit(sPH30HourW), 2, mean)
sPH27HourW48=apply(na.omit(sPH27HourW), 2, mean)
sPH35HourW48=apply(na.omit(sPH35HourW), 2, mean)
sPH43HourW48=apply(na.omit(sPH43HourW), 2, mean)
sPH33HourW48=apply(na.omit(sPH33HourW), 2, mean)
sPH11HourW48=apply(na.omit(sPH11HourW), 2, mean)
sPH22HourW48=apply(na.omit(sPH22HourW), 2, mean)
sPH17HourW48=apply(na.omit(sPH17HourW), 2, mean)
sPH31HourW48=apply(na.omit(sPH31HourW), 2, mean)
sPH26HourW48=apply(na.omit(sPH25HourW), 2, mean)
sPH14HourW48=apply(na.omit(sPH14HourW), 2, mean)
sPH19HourW48=apply(na.omit(sPH19HourW), 2, mean)
sPH12HourW48=apply(na.omit(sPH12HourW), 2, mean)
sPH49HourW48=apply(na.omit(sPH49HourW), 2, mean)
sPH20HourW48=apply(na.omit(sPH20HourW), 2, mean)
sPH36HourW48=apply(na.omit(sPH36HourW), 2, mean)

#Making 1 hour average 
# DEclaring varibales
sPH25HourW24x=rep(NA, 24)
sPH29HourW24x=rep(NA, 24)
sPH30HourW24x=rep(NA, 24)
sPH27HourW24x=rep(NA, 24)
sPH35HourW24x=rep(NA, 24)
sPH43HourW24x=rep(NA, 24)
sPH33HourW24x=rep(NA, 24)
sPH11HourW24x=rep(NA, 24)
sPH22HourW24x=rep(NA, 24)
sPH17HourW24x=rep(NA, 24)
sPH31HourW24x=rep(NA, 24)
sPH26HourW24x=rep(NA, 24)
sPH14HourW24x=rep(NA, 24)
sPH19HourW24x=rep(NA, 24)
sPH12HourW24x=rep(NA, 24)
sPH49HourW24x=rep(NA, 24)
sPH20HourW24x=rep(NA, 24)
sPH36HourW24x=rep(NA, 24)

  for (i in 1:24){
    sPH25HourW24x[i]=(sPH25HourW48[2*i-1]+sPH25HourW48[2*i])*0.5
    sPH29HourW24x[i]=(sPH29HourW48[2*i-1]+sPH29HourW48[2*i])*0.5
    sPH30HourW24x[i]=(sPH30HourW48[2*i-1]+sPH30HourW48[2*i])*0.5
    sPH27HourW24x[i]=(sPH27HourW48[2*i-1]+sPH27HourW48[2*i])*0.5
    sPH35HourW24x[i]=(sPH35HourW48[2*i-1]+sPH35HourW48[2*i])*0.5
    sPH43HourW24x[i]=(sPH43HourW48[2*i-1]+sPH43HourW48[2*i])*0.5
    sPH33HourW24x[i]=(sPH33HourW48[2*i-1]+sPH33HourW48[2*i])*0.5
    sPH11HourW24x[i]=(sPH11HourW48[2*i-1]+sPH11HourW48[2*i])*0.5
    sPH22HourW24x[i]=(sPH22HourW48[2*i-1]+sPH22HourW48[2*i])*0.5
    sPH17HourW24x[i]=(sPH17HourW48[2*i-1]+sPH17HourW48[2*i])*0.5
    sPH31HourW24x[i]=(sPH31HourW48[2*i-1]+sPH31HourW48[2*i])*0.5
    sPH26HourW24x[i]=(sPH26HourW48[2*i-1]+sPH26HourW48[2*i])*0.5
    sPH14HourW24x[i]=(sPH14HourW48[2*i-1]+sPH14HourW48[2*i])*0.5
    sPH19HourW24x[i]=(sPH19HourW48[2*i-1]+sPH19HourW48[2*i])*0.5
    sPH12HourW24x[i]=(sPH12HourW48[2*i-1]+sPH12HourW48[2*i])*0.5
    sPH49HourW24x[i]=(sPH49HourW48[2*i-1]+sPH49HourW48[2*i])*0.5
    sPH20HourW24x[i]=(sPH20HourW48[2*i-1]+sPH20HourW48[2*i])*0.5
    sPH36HourW24x[i]=(sPH36HourW48[2*i-1]+sPH36HourW48[2*i])*0.5

  }
 


# Conductivity



sCON25HourW48=apply(na.omit(sCON25HourW), 2, mean)
sCON29HourW48=apply(na.omit(sCON29HourW), 2, mean)
sCON30HourW48=apply(na.omit(sCON30HourW), 2, mean)
sCON27HourW48=apply(na.omit(sCON27HourW), 2, mean)
sCON35HourW48=apply(na.omit(sCON35HourW), 2, mean)
sCON43HourW48=apply(na.omit(sCON43HourW), 2, mean)
sCON33HourW48=apply(na.omit(sCON33HourW), 2, mean)
sCON11HourW48=apply(na.omit(sCON11HourW), 2, mean)
sCON22HourW48=apply(na.omit(sCON22HourW), 2, mean)
sCON17HourW48=apply(na.omit(sCON17HourW), 2, mean)
sCON31HourW48=apply(na.omit(sCON31HourW), 2, mean)
sCON26HourW48=apply(na.omit(sCON25HourW), 2, mean)
sCON14HourW48=apply(na.omit(sCON14HourW), 2, mean)
sCON19HourW48=apply(na.omit(sCON19HourW), 2, mean)
sCON12HourW48=apply(na.omit(sCON12HourW), 2, mean)
sCON49HourW48=apply(na.omit(sCON49HourW), 2, mean)
sCON20HourW48=apply(na.omit(sCON20HourW), 2, mean)
sCON36HourW48=apply(na.omit(sCON36HourW), 2, mean)

#Making 1 hour average 
# DEclaring varibales
sCON25HourW24x=rep(NA, 24)
sCON29HourW24x=rep(NA, 24)
sCON30HourW24x=rep(NA, 24)
sCON27HourW24x=rep(NA, 24)
sCON35HourW24x=rep(NA, 24)
sCON43HourW24x=rep(NA, 24)
sCON33HourW24x=rep(NA, 24)
sCON11HourW24x=rep(NA, 24)
sCON22HourW24x=rep(NA, 24)
sCON17HourW24x=rep(NA, 24)
sCON31HourW24x=rep(NA, 24)
sCON26HourW24x=rep(NA, 24)
sCON14HourW24x=rep(NA, 24)
sCON19HourW24x=rep(NA, 24)
sCON12HourW24x=rep(NA, 24)
sCON49HourW24x=rep(NA, 24)
sCON20HourW24x=rep(NA, 24)
sCON36HourW24x=rep(NA, 24)

  for (i in 1:24){
    sCON25HourW24x[i]=(sCON25HourW48[2*i-1]+sCON25HourW48[2*i])*0.5
    sCON29HourW24x[i]=(sCON29HourW48[2*i-1]+sCON29HourW48[2*i])*0.5
    sCON30HourW24x[i]=(sCON30HourW48[2*i-1]+sCON30HourW48[2*i])*0.5
    sCON27HourW24x[i]=(sCON27HourW48[2*i-1]+sCON27HourW48[2*i])*0.5
    sCON35HourW24x[i]=(sCON35HourW48[2*i-1]+sCON35HourW48[2*i])*0.5
    sCON43HourW24x[i]=(sCON43HourW48[2*i-1]+sCON43HourW48[2*i])*0.5
    sCON33HourW24x[i]=(sCON33HourW48[2*i-1]+sCON33HourW48[2*i])*0.5
    sCON11HourW24x[i]=(sCON11HourW48[2*i-1]+sCON11HourW48[2*i])*0.5
    sCON22HourW24x[i]=(sCON22HourW48[2*i-1]+sCON22HourW48[2*i])*0.5
    sCON17HourW24x[i]=(sCON17HourW48[2*i-1]+sCON17HourW48[2*i])*0.5
    sCON31HourW24x[i]=(sCON31HourW48[2*i-1]+sCON31HourW48[2*i])*0.5
    sCON26HourW24x[i]=(sCON26HourW48[2*i-1]+sCON26HourW48[2*i])*0.5
    sCON14HourW24x[i]=(sCON14HourW48[2*i-1]+sCON14HourW48[2*i])*0.5
    sCON19HourW24x[i]=(sCON19HourW48[2*i-1]+sCON19HourW48[2*i])*0.5
    sCON12HourW24x[i]=(sCON12HourW48[2*i-1]+sCON12HourW48[2*i])*0.5
    sCON49HourW24x[i]=(sCON49HourW48[2*i-1]+sCON49HourW48[2*i])*0.5
    sCON20HourW24x[i]=(sCON20HourW48[2*i-1]+sCON20HourW48[2*i])*0.5
    sCON36HourW24x[i]=(sCON36HourW48[2*i-1]+sCON36HourW48[2*i])*0.5

  }
 




```

## Make Simulation data as 24 hour average data


```{r}

#Notes: CSV files has been proceed on R on Plot_compare.rmd on VM
par(mfrow=c(1,1))
stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
fn="cNH2CL_TOC1_AllNodes.csv"
# fn1="cNH2CL_Auto.csv"
# fn2="cNH2CL_NO2_NO3.csv"
# fn3="cNH2CL_NO2_NO3_w.csv"
# fn4="cNH2CL_NO2_NO3_w_TOC02.csv" # 0.2 mg/L TOC
# fn5="cNH2CL_NO2_NO3_w_TOC05.csv"
# fn6="cNH2CL_NO2_NO3_w_TOC1.csv"
# fn7="cNH2CL_NO2_NO3_w_TOC2.csv"
# fn8="cNH2CL_NO2_NO3_w_TOC3.csv"


fn<- read.table(fn, header = FALSE, sep = ",", nrow=length(stnLoc), fill=TRUE)

# 24 hr was avoided while maing csv file (see VM) agnain another 2 days avod

#stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)

fn_25<-as.numeric(fn[1,194:217])
fn_29<-as.numeric(fn[2,194:217])
fn_30<-as.numeric(fn[3,194:217])
fn_27<-as.numeric(fn[4,194:217])
fn_35<-as.numeric(fn[5,194:217])
fn_43<-as.numeric(fn[6,194:217])
fn_33<-as.numeric(fn[7,194:217])
fn_11<-as.numeric(fn[8,194:217])

fn_22<-as.numeric(fn[9,194:217])
fn_17<-as.numeric(fn[10,194:217])
fn_31<-as.numeric(fn[11,194:217])
fn_26<-as.numeric(fn[12,194:217])
fn_14<-as.numeric(fn[13,194:217])
fn_19<-as.numeric(fn[14,194:217])
fn_12<-as.numeric(fn[15,194:217])
fn_49<-as.numeric(fn[16,194:217])

fn_20<-as.numeric(fn[17,194:217])
fn_36<-as.numeric(fn[18,194:217])





par(mfrow=c(1,1))
#plot(dTime, sORP35, type='n')

ylm1=c(0,3)


#NH2CL
plot(1:24, fn_35, col="red", type='l', yaxt='n',  ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(1:24, fn_25, col="green", type='l',axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(1:24, fn_30, col="blue", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(1:24, fn_17, col="brown", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)
par(new=T)
plot(1:24, fn_14, col="purple", type='l', axes=FALSE, ylim=ylm1, xlab = "", ylab = "")
axis(2, ylim=ylm1, col="black",las=1)

legend("bottomright", lty=c(1,1), col=c("red", "green","blue","brown","purple"), legend=c("35", "25", "30", "17", "14"))
title("Daily NH2CL with time in different stations")
mtext("Time ",side=1,col="black",line=2.5) 
mtext("NH2CL ",side=2,col="black",line=2.5)
















#stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
#NH2CL vs PH
par(mfrow=c(1,1))

reg25PH<-lm(sPH25HourW24x~fn_25)
plot(fn_25,sPH25HourW24x,  xlab = "", ylab = "")
abline(reg25PH)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5)

reg29PH<-lm(sPH29HourW24x~fn_29)
plot(fn_29,sPH29HourW24x,  xlab = "", ylab = "")
abline(reg29PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg30PH<-lm(sPH30HourW24x~fn_30)
plot(fn_30,sPH30HourW24x,  xlab = "", ylab = "")
abline(reg30PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg27PH<-lm(sPH27HourW24x~fn_27)
plot(fn_27,sPH27HourW24x,  xlab = "", ylab = "")
abline(reg27PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg35PH<-lm(sPH35HourW24x~fn_35)
plot(fn_35,sPH35HourW24x,  xlab = "", ylab = "")
abline(reg35PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg43PH<-lm(sPH43HourW24x~fn_43)
plot(fn_43,sPH43HourW24x,  xlab = "", ylab = "")
abline(reg43PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)
#stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
reg33PH<-lm(sPH33HourW24x~fn_33)
plot(fn_33,sPH33HourW24x,  xlab = "", ylab = "")
abline(reg33PH) 
mtext("NH2Cl(mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg11PH<-lm(sPH11HourW24x~fn_11)
plot(fn_11,sPH11HourW24x,  xlab = "", ylab = "")
abline(reg11PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg22PH<-lm(sPH22HourW24x~fn_22)
plot(fn_22,sPH22HourW24x,  xlab = "", ylab = "")
abline(reg22PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)


reg17PH<-lm(sPH17HourW24x~fn_17)
plot(fn_17,sPH17HourW24x,  xlab = "", ylab = "")
abline(reg17PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)


reg31PH<-lm(sPH31HourW24x~fn_31)
plot(fn_31,sPH31HourW24x,  xlab = "", ylab = "")
abline(reg31PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg26PH<-lm(sPH26HourW24x~fn_26)
plot(fn_26,sPH26HourW24x,  xlab = "", ylab = "")
abline(reg26PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg14PH<-lm(sPH14HourW24x~fn_14)
plot(fn_14,sPH14HourW24x,  xlab = "", ylab = "")
abline(reg14PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg19PH<-lm(sPH19HourW24x~fn_19)
plot(fn_19,sPH19HourW24x,  xlab = "", ylab = "")
abline(reg19PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg12PH<-lm(sPH12HourW24x~fn_12)
plot(fn_12,sPH12HourW24x,  xlab = "", ylab = "")
abline(reg12PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg49PH<-lm(sPH49HourW24x~fn_49)
plot(fn_49,sPH49HourW24x,  xlab = "", ylab = "")
abline(reg49PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg20PH<-lm(sPH20HourW24x~fn_20)
plot(fn_20,sPH20HourW24x,  xlab = "", ylab = "")
abline(reg20PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)

reg36PH<-lm(sPH36HourW24x~fn_36)
plot(fn_36,sPH36HourW24x,  xlab = "", ylab = "")
abline(reg36PH) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("pH ",side=2,col="black",line=2.5)




#NH2CL vs ORP
reg25ORP<-lm(sORP25HourW24x~fn_25)
plot(fn_25,sORP25HourW24x,  xlab = "", ylab = "")
abline(reg25ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)



reg29ORP<-lm(sORP29HourW24x~fn_29)
plot(fn_29,sORP29HourW24x,  xlab = "", ylab = "")
abline(reg29ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg30ORP<-lm(sORP30HourW24x~fn_30)
plot(fn_30,sORP30HourW24x,  xlab = "", ylab = "")
abline(reg30ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg27ORP<-lm(sORP27HourW24x~fn_27)
plot(fn_27,sORP27HourW24x,  xlab = "", ylab = "")
abline(reg27ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg35ORP<-lm(sORP35HourW24x~fn_35)
plot(fn_35,sORP35HourW24x,  xlab = "", ylab = "")
abline(reg35ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg43ORP<-lm(sORP43HourW24x~fn_43)
plot(fn_43,sORP43HourW24x,  xlab = "", ylab = "")
abline(reg43ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)
#stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
reg33ORP<-lm(sORP33HourW24x~fn_33)
plot(fn_33,sORP33HourW24x,  xlab = "", ylab = "")
abline(reg33ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg11ORP<-lm(sORP11HourW24x~fn_11)
plot(fn_11,sORP11HourW24x,  xlab = "", ylab = "")
abline(reg11ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg22ORP<-lm(sORP22HourW24x~fn_22)
plot(fn_22,sORP22HourW24x,  xlab = "", ylab = "")
abline(reg22ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)


reg17ORP<-lm(sORP17HourW24x~fn_17)
plot(fn_17,sORP17HourW24x,  xlab = "", ylab = "")
abline(reg17ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)


reg31ORP<-lm(sORP31HourW24x~fn_31)
plot(fn_31,sORP31HourW24x,  xlab = "", ylab = "")
abline(reg31ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg26ORP<-lm(sORP26HourW24x~fn_26)
plot(fn_26,sORP26HourW24x,  xlab = "", ylab = "")
abline(reg26ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg14ORP<-lm(sORP14HourW24x~fn_14)
plot(fn_14,sORP14HourW24x,  xlab = "", ylab = "")
abline(reg14ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg19ORP<-lm(sORP19HourW24x~fn_19)
plot(fn_19,sORP19HourW24x,  xlab = "", ylab = "")
abline(reg19ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg12ORP<-lm(sORP12HourW24x~fn_12)
plot(fn_12,sORP12HourW24x,  xlab = "", ylab = "")
abline(reg12ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg49ORP<-lm(sORP49HourW24x~fn_49)
plot(fn_49,sORP49HourW24x,  xlab = "", ylab = "")
abline(reg49ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg20ORP<-lm(sORP20HourW24x~fn_20)
plot(fn_20,sORP20HourW24x,  xlab = "", ylab = "")
abline(reg20ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

reg36ORP<-lm(sORP36HourW24x~fn_36)
plot(fn_36,sORP36HourW24x,  xlab = "", ylab = "")
abline(reg36ORP) 
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5)  
mtext("ORP",side=2,col="black",line=2.5)

```
#ORP vs PH

### Excellent relationship observed in ORP vs PH
```{r}

par(mfrow=c(1,1))


#ORP vs PH

reg25ORP<-lm(sORP25HourW24x~sPH25HourW24x)
plot(sPH25HourW24x,sORP25HourW24x,  xlab = "", ylab = "")
abline(reg25ORP)


reg29ORP<-lm(sORP29HourW24x~sPH29HourW24x)
plot(sPH29HourW24x,sORP29HourW24x,  xlab = "", ylab = "")
abline(reg29ORP)

reg30ORP<-lm(sORP30HourW24x~sPH30HourW24x)
plot(sPH30HourW24x,sORP30HourW24x,  xlab = "", ylab = "")
abline(reg30ORP)

reg27ORP<-lm(sORP27HourW24x~sPH27HourW24x)
plot(sPH27HourW24x,sORP27HourW24x,  xlab = "", ylab = "")
abline(reg27ORP)

reg35ORP<-lm(sORP35HourW24x~sPH35HourW24x)
plot(sPH35HourW24x,sORP35HourW24x,  xlab = "", ylab = "")
abline(reg35ORP)

reg43ORP<-lm(sORP43HourW24x~sPH43HourW24x)
plot(sPH43HourW24x,sORP43HourW24x,  xlab = "", ylab = "")
abline(reg43ORP)
#stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
reg33ORP<-lm(sORP33HourW24x~sPH33HourW24x)
plot(sPH33HourW24x,sORP33HourW24x,  xlab = "", ylab = "")
abline(reg33ORP)

reg11ORP<-lm(sORP11HourW24x~sPH11HourW24x)
plot(sPH11HourW24x,sORP11HourW24x,  xlab = "", ylab = "")
abline(reg11ORP)

reg22ORP<-lm(sORP22HourW24x~sPH22HourW24x)
plot(sPH22HourW24x,sORP22HourW24x,  xlab = "", ylab = "")
abline(reg22ORP)


reg17ORP<-lm(sORP17HourW24x~sPH17HourW24x)
plot(sPH17HourW24x,sORP17HourW24x,  xlab = "", ylab = "")
abline(reg17ORP)


reg31ORP<-lm(sORP31HourW24x~sPH31HourW24x)
plot(sPH31HourW24x,sORP31HourW24x,  xlab = "", ylab = "")
abline(reg31ORP)

reg26ORP<-lm(sORP26HourW24x~sPH26HourW24x)
plot(sPH26HourW24x,sORP26HourW24x,  xlab = "", ylab = "")
abline(reg26ORP)

reg14ORP<-lm(sORP14HourW24x~sPH14HourW24x)
plot(sPH14HourW24x,sORP14HourW24x,  xlab = "", ylab = "")
abline(reg14ORP)

reg19ORP<-lm(sORP19HourW24x~sPH19HourW24x)
plot(sPH19HourW24x,sORP19HourW24x,  xlab = "", ylab = "")
abline(reg19ORP)

reg12ORP<-lm(sORP12HourW24x~fn_12)
plot(fn_12,sORP12HourW24x,  xlab = "", ylab = "")
abline(reg12ORP)

reg49ORP<-lm(sORP49HourW24x~sPH49HourW24x)
plot(sPH49HourW24x,sORP49HourW24x,  xlab = "", ylab = "")
abline(reg49ORP)

reg20ORP<-lm(sORP20HourW24x~sPH20HourW24x)
plot(sPH20HourW24x,sORP20HourW24x,  xlab = "", ylab = "")
abline(reg20ORP)

reg36ORP<-lm(sORP36HourW24x~sPH36HourW24x)
plot(sPH36HourW24x,sORP36HourW24x,  xlab = "", ylab = "")
abline(reg36ORP)











```

# ORP vs Conductivity

```{r}

par(mfrow=c(1,1))


#ORP vs CON

reg25ORP<-lm(sORP25HourW24x~sCON25HourW24x)
plot(sCON25HourW24x,sORP25HourW24x,  xlab = "", ylab = "")
abline(reg25ORP)


reg29ORP<-lm(sORP29HourW24x~sCON29HourW24x)
plot(sCON29HourW24x,sORP29HourW24x,  xlab = "", ylab = "")
abline(reg29ORP)

reg30ORP<-lm(sORP30HourW24x~sCON30HourW24x)
plot(sCON30HourW24x,sORP30HourW24x,  xlab = "", ylab = "")
abline(reg30ORP)

reg27ORP<-lm(sORP27HourW24x~sCON27HourW24x)
plot(sCON27HourW24x,sORP27HourW24x,  xlab = "", ylab = "")
abline(reg27ORP)

reg35ORP<-lm(sORP35HourW24x~sCON35HourW24x)
plot(sCON35HourW24x,sORP35HourW24x,  xlab = "", ylab = "")
abline(reg35ORP)

reg43ORP<-lm(sORP43HourW24x~sCON43HourW24x)
plot(sCON43HourW24x,sORP43HourW24x,  xlab = "", ylab = "")
abline(reg43ORP)
#stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
reg33ORP<-lm(sORP33HourW24x~sCON33HourW24x)
plot(sCON33HourW24x,sORP33HourW24x,  xlab = "", ylab = "")
abline(reg33ORP)

reg11ORP<-lm(sORP11HourW24x~sCON11HourW24x)
plot(sCON11HourW24x,sORP11HourW24x,  xlab = "", ylab = "")
abline(reg11ORP)

reg22ORP<-lm(sORP22HourW24x~sCON22HourW24x)
plot(sCON22HourW24x,sORP22HourW24x,  xlab = "", ylab = "")
abline(reg22ORP)


reg17ORP<-lm(sORP17HourW24x~sCON17HourW24x)
plot(sCON17HourW24x,sORP17HourW24x,  xlab = "", ylab = "")
abline(reg17ORP)


reg31ORP<-lm(sORP31HourW24x~sCON31HourW24x)
plot(sCON31HourW24x,sORP31HourW24x,  xlab = "", ylab = "")
abline(reg31ORP)

reg26ORP<-lm(sORP26HourW24x~sCON26HourW24x)
plot(sCON26HourW24x,sORP26HourW24x,  xlab = "", ylab = "")
abline(reg26ORP)

reg14ORP<-lm(sORP14HourW24x~sCON14HourW24x)
plot(sCON14HourW24x,sORP14HourW24x,  xlab = "", ylab = "")
abline(reg14ORP)

reg19ORP<-lm(sORP19HourW24x~sCON19HourW24x)
plot(sCON19HourW24x,sORP19HourW24x,  xlab = "", ylab = "")
abline(reg19ORP)

reg12ORP<-lm(sORP12HourW24x~fn_12)
plot(fn_12,sORP12HourW24x,  xlab = "", ylab = "")
abline(reg12ORP)

reg49ORP<-lm(sORP49HourW24x~sCON49HourW24x)
plot(sCON49HourW24x,sORP49HourW24x,  xlab = "", ylab = "")
abline(reg49ORP)

reg20ORP<-lm(sORP20HourW24x~sCON20HourW24x)
plot(sCON20HourW24x,sORP20HourW24x,  xlab = "", ylab = "")
abline(reg20ORP)

reg36ORP<-lm(sORP36HourW24x~sCON36HourW24x)
plot(sCON36HourW24x,sORP36HourW24x,  xlab = "", ylab = "")
abline(reg36ORP)





```

CON vs PH
```{r}
par(mfrow=c(1,1))


#ORP vs PH

reg25CON<-lm(sCON25HourW24x~sPH25HourW24x)
plot(sPH25HourW24x,sCON25HourW24x,  xlab = "", ylab = "")
abline(reg25CON)


reg29CON<-lm(sCON29HourW24x~sPH29HourW24x)
plot(sPH29HourW24x,sCON29HourW24x,  xlab = "", ylab = "")
abline(reg29CON)

reg30CON<-lm(sCON30HourW24x~sPH30HourW24x)
plot(sPH30HourW24x,sCON30HourW24x,  xlab = "", ylab = "")
abline(reg30CON)

reg27CON<-lm(sCON27HourW24x~sPH27HourW24x)
plot(sPH27HourW24x,sCON27HourW24x,  xlab = "", ylab = "")
abline(reg27CON)

reg35CON<-lm(sCON35HourW24x~sPH35HourW24x)
plot(sPH35HourW24x,sCON35HourW24x,  xlab = "", ylab = "")
abline(reg35CON)

reg43CON<-lm(sCON43HourW24x~sPH43HourW24x)
plot(sPH43HourW24x,sCON43HourW24x,  xlab = "", ylab = "")
abline(reg43CON)
#stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
reg33CON<-lm(sCON33HourW24x~sPH33HourW24x)
plot(sPH33HourW24x,sCON33HourW24x,  xlab = "", ylab = "")
abline(reg33CON)

reg11CON<-lm(sCON11HourW24x~sPH11HourW24x)
plot(sPH11HourW24x,sCON11HourW24x,  xlab = "", ylab = "")
abline(reg11CON)

reg22CON<-lm(sCON22HourW24x~sPH22HourW24x)
plot(sPH22HourW24x,sCON22HourW24x,  xlab = "", ylab = "")
abline(reg22CON)


reg17CON<-lm(sCON17HourW24x~sPH17HourW24x)
plot(sPH17HourW24x,sCON17HourW24x,  xlab = "", ylab = "")
abline(reg17CON)


reg31CON<-lm(sCON31HourW24x~sPH31HourW24x)
plot(sPH31HourW24x,sCON31HourW24x,  xlab = "", ylab = "")
abline(reg31CON)

reg26CON<-lm(sCON26HourW24x~sPH26HourW24x)
plot(sPH26HourW24x,sCON26HourW24x,  xlab = "", ylab = "")
abline(reg26CON)

reg14CON<-lm(sCON14HourW24x~sPH14HourW24x)
plot(sPH14HourW24x,sCON14HourW24x,  xlab = "", ylab = "")
abline(reg14CON)

reg19CON<-lm(sCON19HourW24x~sPH19HourW24x)
plot(sPH19HourW24x,sCON19HourW24x,  xlab = "", ylab = "")
abline(reg19CON)

reg12CON<-lm(sCON12HourW24x~fn_12)
plot(fn_12,sCON12HourW24x,  xlab = "", ylab = "")
abline(reg12CON)

reg49CON<-lm(sCON49HourW24x~sPH49HourW24x)
plot(sPH49HourW24x,sCON49HourW24x,  xlab = "", ylab = "")
abline(reg49CON)

reg20CON<-lm(sCON20HourW24x~sPH20HourW24x)
plot(sPH20HourW24x,sCON20HourW24x,  xlab = "", ylab = "")
abline(reg20CON)

reg36CON<-lm(sCON36HourW24x~sPH36HourW24x)
plot(sPH36HourW24x,sCON36HourW24x,  xlab = "", ylab = "")
abline(reg36CON)




```


# ORP, MCM and pH Together

```{r}

par(mar=c(5.1,4.1,4.1,4))
#25#####################################################
reg25PH<-lm(sPH25HourW24x~fn_25)
plot(fn_25,sPH25HourW24x, type='p', pch=24, yaxt='n', col='green', xlab = "", ylab = "")
abline(reg25PH, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg25ORP<-lm(sORP25HourW24x~fn_25)
plot(fn_25,sORP25HourW24x, type='p', pch=18,axes=FALSE, col='red', xlab = "", ylab = "")
abline(reg25ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)

#29#####################################################
reg29PH<-lm(sPH29HourW24x~fn_29)
plot(fn_29,sPH29HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg29PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg29ORP<-lm(sORP29HourW24x~fn_29)
plot(fn_29,sORP29HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg29ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)



#30#####################################################
reg30PH<-lm(sPH30HourW24x~fn_30)
plot(fn_30,sPH30HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg30PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg30ORP<-lm(sORP30HourW24x~fn_30)
plot(fn_30,sORP30HourW24x, type='p', pch=18,yaxt='n', col='red' ,xlab = "", ylab = "")
abline(reg30ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#27#####################################################
reg27PH<-lm(sPH27HourW24x~fn_27)
plot(fn_27,sPH27HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg27PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg27ORP<-lm(sORP27HourW24x~fn_27)
plot(fn_27,sORP27HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg27ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)

#35#####################################################
reg35PH<-lm(sPH35HourW24x~fn_35)
plot(fn_35,sPH35HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg35PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg35ORP<-lm(sORP35HourW24x~fn_35)
plot(fn_35,sORP35HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg35ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)

#43#####################################################
reg43PH<-lm(sPH43HourW24x~fn_43)
plot(fn_43,sPH43HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg43PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg43ORP<-lm(sORP43HourW24x~fn_43)
plot(fn_43,sORP43HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg43ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#33#####################################################
reg33PH<-lm(sPH33HourW24x~fn_33)
plot(fn_33,sPH33HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg33PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg33ORP<-lm(sORP33HourW24x~fn_33)
plot(fn_33,sORP33HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg33ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#11#####################################################
reg11PH<-lm(sPH11HourW24x~fn_11)
plot(fn_11,sPH11HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg11PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg11ORP<-lm(sORP11HourW24x~fn_11)
plot(fn_11,sORP11HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg11ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#22#####################################################
reg22PH<-lm(sPH22HourW24x~fn_22)
plot(fn_22,sPH22HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg22PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg22ORP<-lm(sORP22HourW24x~fn_22)
plot(fn_22,sORP22HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg22ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)


#stnLoc<-c(25, 29, 30, 27, 35, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
#17#####################################################
reg17PH<-lm(sPH17HourW24x~fn_17)
plot(fn_17,sPH17HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg17PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg17ORP<-lm(sORP17HourW24x~fn_17)
plot(fn_17,sORP17HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg17ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#31#####################################################
reg31PH<-lm(sPH31HourW24x~fn_31)
plot(fn_31,sPH31HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg31PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg31ORP<-lm(sORP31HourW24x~fn_31)
plot(fn_31,sORP31HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg31ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)

#26#####################################################
reg26PH<-lm(sPH26HourW24x~fn_26)
plot(fn_26,sPH26HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg26PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg26ORP<-lm(sORP26HourW24x~fn_26)
plot(fn_26,sORP26HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg26ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#14#####################################################
reg14PH<-lm(sPH14HourW24x~fn_14)
plot(fn_14,sPH14HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg14PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)
#stnLoc<-c(25, 29, 30, 27, 14, 43, 33,11,22,17,31,26,14,19,12,49,20,36)
reg14ORP<-lm(sORP14HourW24x~fn_14)
plot(fn_14,sORP14HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg14ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#19#####################################################
reg19PH<-lm(sPH19HourW24x~fn_19)
plot(fn_19,sPH19HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg19PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg19ORP<-lm(sORP19HourW24x~fn_19)
plot(fn_19,sORP19HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg19ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#12#####################################################
reg12PH<-lm(sPH12HourW24x~fn_12)
plot(fn_12,sPH12HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg12PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg12ORP<-lm(sORP12HourW24x~fn_12)
plot(fn_12,sORP12HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg12ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#49#####################################################
reg49PH<-lm(sPH49HourW24x~fn_49)
plot(fn_49,sPH49HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg49PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg49ORP<-lm(sORP49HourW24x~fn_49)
plot(fn_49,sORP49HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg49ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#20#####################################################
reg20PH<-lm(sPH20HourW24x~fn_20)
plot(fn_20,sPH20HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg20PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg20ORP<-lm(sORP20HourW24x~fn_20 ,xlab = "", ylab = "")
plot(fn_20,sORP20HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg20ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)
#36#####################################################
reg36PH<-lm(sPH36HourW24x~fn_36)
plot(fn_36,sPH36HourW24x, type='p', pch=24, yaxt='n', col='green' ,xlab = "", ylab = "")
abline(reg36PH, axes=FALSE, col='green')
axis(2, ylim=c(8,10),col="black",las=1)
par(new=T)

reg36ORP<-lm(sORP36HourW24x~fn_36)
plot(fn_36,sORP36HourW24x, type='p', pch=18,axes=FALSE, col='red' ,xlab = "", ylab = "")
abline(reg36ORP,axes=FALSE, col='red')
axis(4, ylim=c(300,600),col="black",las=1)
mtext("NH2CL (mg/L) ",side=1,col="black",line=2.5) 
mtext("pH ",side=2,col="black",line=2.5) 
mtext("ORP ",side=4,col="black",line=2.5)

```







## Each Hour Analysis
```{r}
set.seed(1221113)
 par(mar=rep(3, 4), mfrow=c(3,1))
 # 1 indicate time at 12:00, 18: 9:00 am , 3: "17pm"

 plot(sORP25HourW[,1]);lines(1:62, sORP25HourW[,1], type="l", col="red", main= "S25"); par(new=TRUE)
 plot(sORP25HourW[,18]);lines(1:62, sORP25HourW[,18], type="l", col="red")
 plot(sORP25HourW[,36]);lines(1:62, sORP25HourW[,36], type="l", col="red")

plot(sCON25HourW[,1]);lines(1:62, sCON25HourW[,1], type="l", col="red")
plot(sCON25HourW[,18]);lines(1:62, sCON25HourW[,18], type="l", col="red")
plot(sCON25HourW[,36]);lines(1:62, sCON25HourW[,36], type="l", col="red")
 
 
 plot(sPH25HourW[,1]);lines(1:61, sPH25HourW[,1], type="l", col="red")
 plot(sPH25HourW[,18]);lines(1:61, sPH25HourW[,18], type="l", col="red")
 plot(sPH25HourW[,36]);lines(1:61, sPH25HourW[,36], type="l", col="red")




plot(sORP29HourW[,1]);lines(1:62, sORP29HourW[,1], type="l", col="red", main= "S29")
 plot(sORP29HourW[,18]);lines(1:62, sORP29HourW[,18], type="l", col="red")
 plot(sORP29HourW[,36]);lines(1:62, sORP29HourW[,36], type="l", col="red")

plot(sCON29HourW[,1]);lines(1:62, sCON29HourW[,1], type="l", col="red")
plot(sCON29HourW[,18]);lines(1:62, sCON29HourW[,18], type="l", col="red")
 plot(sCON29HourW[,36]);lines(1:62, sCON29HourW[,36], type="l", col="red")
 
 plot(sPH29HourW[,1]);lines(1:61, sPH29HourW[,1], type="l", col="red")
 plot(sPH29HourW[,18]);lines(1:61, sPH29HourW[,18], type="l", col="red")
 plot(sPH29HourW[,36]);lines(1:61, sPH29HourW[,36], type="l", col="red")



plot(sORP30HourW[,1]);lines(1:62, sORP30HourW[,1], type="l", col="red", main= "S30")
 plot(sORP30HourW[,18]);lines(1:62, sORP30HourW[,18], type="l", col="red")
 plot(sORP30HourW[,36]);lines(1:62, sORP30HourW[,36], type="l", col="red")
 
 plot(sCON30HourW[,1]);lines(1:62, sCON30HourW[,1], type="l", col="red")
 plot(sCON30HourW[,18]);lines(1:62, sCON30HourW[,18], type="l", col="red")
plot(sCON30HourW[,36]);lines(1:62, sCON30HourW[,36], type="l", col="red")

 plot(sPH30HourW[,1]);lines(1:61, sPH30HourW[,1], type="l", col="red")
 plot(sPH30HourW[,18]);lines(1:61, sPH30HourW[,18], type="l", col="red")
 plot(sPH30HourW[,36]);lines(1:61, sPH30HourW[,36], type="l", col="red")



plot(sORP27HourW[,1]);lines(1:62, sORP27HourW[,1], type="l", col="red", main= "S27")
 plot(sORP27HourW[,18]);lines(1:62, sORP27HourW[,18], type="l", col="red")
 plot(sORP27HourW[,36]);lines(1:62, sORP27HourW[,36], type="l", col="red")
 
plot(sCON27HourW[,1]);lines(1:62, sCON27HourW[,1], type="l", col="red")
plot(sCON27HourW[,18]);lines(1:62, sCON27HourW[,18], type="l", col="red")
plot(sCON27HourW[,36]);lines(1:62, sCON27HourW[,36], type="l", col="red")
 
 plot(sPH27HourW[,1]);lines(1:61, sPH27HourW[,1], type="l", col="red")
 plot(sPH27HourW[,18]);lines(1:61, sPH27HourW[,18], type="l", col="red")
 plot(sPH27HourW[,36]);lines(1:61, sPH27HourW[,36], type="l", col="red")



plot(sORP35HourW[,1]);lines(1:62, sORP35HourW[,1], type="l", col="red", main= "S35")
 plot(sORP35HourW[,18]);lines(1:62, sORP35HourW[,18], type="l", col="red")
 plot(sORP35HourW[,36]);lines(1:62, sORP35HourW[,36], type="l", col="red")
 
plot(sCON35HourW[,1]);lines(1:62, sCON35HourW[,1], type="l", col="red")
 plot(sCON35HourW[,18]);lines(1:62, sCON35HourW[,18], type="l", col="red")
 plot(sCON35HourW[,36]);lines(1:62, sCON35HourW[,36], type="l", col="red")



 plot(sPH35HourW[,1]);lines(1:61, sPH35HourW[,1], type="l", col="red")
 plot(sPH35HourW[,18]);lines(1:61, sPH35HourW[,18], type="l", col="red")
 plot(sPH35HourW[,36]);lines(1:61, sPH35HourW[,36], type="l", col="red")

plot(sORP43HourW[,1]);lines(1:62, sORP43HourW[,1], type="l", col="red", main= "S43")
 plot(sORP43HourW[,18]);lines(1:62, sORP43HourW[,18], type="l", col="red")
 plot(sORP43HourW[,36]);lines(1:62, sORP43HourW[,36], type="l", col="red")


 plot(sCON43HourW[,1]);lines(1:62, sCON43HourW[,1], type="l", col="red")
 plot(sCON43HourW[,18]);lines(1:62, sCON43HourW[,18], type="l", col="red")
 plot(sCON43HourW[,36]);lines(1:62, sCON43HourW[,36], type="l", col="red")

 plot(sPH43HourW[,1]);lines(1:61, sPH43HourW[,1], type="l", col="red")
 plot(sPH43HourW[,18]);lines(1:61, sPH43HourW[,18], type="l", col="red")
 plot(sPH43HourW[,36]);lines(1:61, sPH43HourW[,36], type="l", col="red")

# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36


plot(sORP33HourW[,1]);lines(1:62, sORP33HourW[,1], type="l", col="red", main= "S33")
 plot(sORP33HourW[,18]);lines(1:62, sORP33HourW[,18], type="l", col="red")
 plot(sORP33HourW[,36]);lines(1:62, sORP33HourW[,36], type="l", col="red")
 
plot(sCON33HourW[,1]);lines(1:62, sCON33HourW[,1], type="l", col="red")
 plot(sCON33HourW[,18]);lines(1:62, sCON33HourW[,18], type="l", col="red")
 plot(sCON33HourW[,36]);lines(1:62, sCON33HourW[,36], type="l", col="red")

 plot(sPH33HourW[,1]);lines(1:61, sPH33HourW[,1], type="l", col="red")
 plot(sPH33HourW[,18]);lines(1:61, sPH33HourW[,18], type="l", col="red")
 plot(sPH33HourW[,36]);lines(1:61, sPH33HourW[,36], type="l", col="red")

 plot(sORP11HourW[,1]);lines(1:62, sORP11HourW[,1], type="l", col="red", main= "S11")
 plot(sORP11HourW[,18]);lines(1:62, sORP11HourW[,18], type="l", col="red")
 plot(sORP11HourW[,36]);lines(1:62, sORP11HourW[,36], type="l", col="red")



plot(sCON11HourW[,1]);lines(1:62, sCON11HourW[,18], type="l", col="red")
plot(sCON11HourW[,18]);lines(1:62, sCON11HourW[,18], type="l", col="red")
 plot(sCON11HourW[,36]);lines(1:62, sCON11HourW[,36], type="l", col="red")
 
 plot(sPH11HourW[,1]);lines(1:61, sPH11HourW[,1], type="l", col="red")
 plot(sPH11HourW[,18]);lines(1:61, sPH11HourW[,18], type="l", col="red")
 plot(sPH11HourW[,36]);lines(1:61, sPH11HourW[,36], type="l", col="red")

plot(sORP22HourW[,1]);lines(1:62, sORP22HourW[,1], type="l", col="red", main= "S22")
 plot(sORP22HourW[,18]);lines(1:62, sORP22HourW[,18], type="l", col="red")
 plot(sORP22HourW[,36]);lines(1:62, sORP22HourW[,36], type="l", col="red")


plot(sCON22HourW[,1]);lines(1:62, sCON22HourW[,1], type="l", col="red")
plot(sCON22HourW[,18]);lines(1:62, sCON22HourW[,18], type="l", col="red")
 plot(sCON22HourW[,36]);lines(1:62, sCON22HourW[,36], type="l", col="red")
 
 plot(sPH22HourW[,1]);lines(1:61, sPH22HourW[,1], type="l", col="red")
 plot(sPH22HourW[,18]);lines(1:61, sPH22HourW[,18], type="l", col="red")
 plot(sPH22HourW[,36]);lines(1:61, sPH22HourW[,36], type="l", col="red")

plot(sORP17HourW[,1]);lines(1:62, sORP17HourW[,1], type="l", col="red", main= "S17")
 plot(sORP17HourW[,18]);lines(1:62, sORP17HourW[,18], type="l", col="red")
 plot(sORP17HourW[,36]);lines(1:62, sORP17HourW[,36], type="l", col="red")


 plot(sCON17HourW[,1]);lines(1:62, sCON17HourW[,1], type="l", col="red")
 plot(sCON17HourW[,18]);lines(1:62, sCON17HourW[,18], type="l", col="red")
 plot(sCON17HourW[,36]);lines(1:62, sCON17HourW[,36], type="l", col="red")

 plot(sPH17HourW[,1]);lines(1:61, sPH17HourW[,1], type="l", col="red")
 plot(sPH17HourW[,18]);lines(1:61, sPH17HourW[,18], type="l", col="red")
 plot(sPH17HourW[,36]);lines(1:61, sPH17HourW[,36], type="l", col="red")


plot(sORP31HourW[,1]);lines(1:62, sORP31HourW[,1], type="l", col="red", main= "S31")
 plot(sORP31HourW[,18]);lines(1:62, sORP31HourW[,18], type="l", col="red")
 plot(sORP31HourW[,36]);lines(1:62, sORP31HourW[,36], type="l", col="red")

 plot(sCON31HourW[,1]);lines(1:62, sCON31HourW[,1], type="l", col="red")
 plot(sCON31HourW[,18]);lines(1:62, sCON31HourW[,18], type="l", col="red")
 plot(sCON31HourW[,36]);lines(1:62, sCON31HourW[,36], type="l", col="red")

 plot(sPH31HourW[,1]);lines(1:61, sPH31HourW[,1], type="l", col="red")
 plot(sPH31HourW[,18]);lines(1:61, sPH31HourW[,18], type="l", col="red")
 plot(sPH31HourW[,36]);lines(1:61, sPH31HourW[,36], type="l", col="red")

plot(sORP26HourW[,1]);lines(1:62, sORP26HourW[,1], type="l", col="red", main= "S26")
 plot(sORP26HourW[,18]);lines(1:62, sORP26HourW[,18], type="l", col="red")
 plot(sORP26HourW[,36]);lines(1:62, sORP26HourW[,36], type="l", col="red")


plot(sCON26HourW[,1]);lines(1:62, sCON26HourW[,1], type="l", col="red")
plot(sCON26HourW[,18]);lines(1:62, sCON26HourW[,18], type="l", col="red")
 plot(sCON26HourW[,36]);lines(1:62, sCON26HourW[,36], type="l", col="red")
 
 plot(sPH26HourW[,1]);lines(1:61, sPH26HourW[,1], type="l", col="red")
 plot(sPH26HourW[,18]);lines(1:61, sPH26HourW[,18], type="l", col="red")
 plot(sPH26HourW[,36]);lines(1:61, sPH26HourW[,36], type="l", col="red")

plot(sORP14HourW[,1]);lines(1:62, sORP14HourW[,1], type="l", col="red", main= "S14")
 plot(sORP14HourW[,18]);lines(1:62, sORP14HourW[,18], type="l", col="red")
 plot(sORP14HourW[,36]);lines(1:62, sORP14HourW[,36], type="l", col="red")

plot(sCON14HourW[,1]);lines(1:62, sCON14HourW[,1], type="l", col="red")
plot(sCON14HourW[,18]);lines(1:62, sCON14HourW[,18], type="l", col="red")
 plot(sCON14HourW[,36]);lines(1:62, sCON14HourW[,36], type="l", col="red")
 
 plot(sPH14HourW[,1]);lines(1:61, sPH14HourW[,1], type="l", col="red")
 plot(sPH14HourW[,18]);lines(1:61, sPH14HourW[,18], type="l", col="red")
 plot(sPH14HourW[,36]);lines(1:61, sPH14HourW[,36], type="l", col="red")

plot(sORP19HourW[,1]);lines(1:62, sORP19HourW[,1], type="l", col="red", main= "S19")
 plot(sORP19HourW[,18]);lines(1:62, sORP19HourW[,18], type="l", col="red")
 plot(sORP19HourW[,36]);lines(1:62, sORP19HourW[,36], type="l", col="red")

plot(sCON19HourW[,1]);lines(1:62, sCON19HourW[,1], type="l", col="red")
plot(sCON19HourW[,18]);lines(1:62, sCON19HourW[,18], type="l", col="red")
 plot(sCON19HourW[,36]);lines(1:62, sCON19HourW[,36], type="l", col="red")
 
 plot(sPH19HourW[,1]);lines(1:61, sPH19HourW[,1], type="l", col="red")
 plot(sPH19HourW[,18]);lines(1:61, sPH19HourW[,18], type="l", col="red")
 plot(sPH19HourW[,36]);lines(1:61, sPH19HourW[,36], type="l", col="red")

plot(sORP12HourW[,1]);lines(1:62, sORP12HourW[,1], type="l", col="red", main= "S12")
 plot(sORP12HourW[,18]);lines(1:62, sORP12HourW[,18], type="l", col="red")
 plot(sORP12HourW[,36]);lines(1:62, sORP12HourW[,36], type="l", col="red")

plot(sCON12HourW[,1]);lines(1:62, sCON12HourW[,1], type="l", col="red")
plot(sCON12HourW[,18]);lines(1:62, sCON12HourW[,18], type="l", col="red")
 plot(sCON12HourW[,36]);lines(1:62, sCON12HourW[,36], type="l", col="red")
 
 plot(sPH12HourW[,1]);lines(1:61, sPH12HourW[,1], type="l", col="red")
 plot(sPH12HourW[,18]);lines(1:61, sPH12HourW[,18], type="l", col="red")
 plot(sPH12HourW[,36]);lines(1:61, sPH12HourW[,36], type="l", col="red")

plot(sORP49HourW[,1]);lines(1:62, sORP49HourW[,1], type="l", col="red", main= "S49")
 plot(sORP49HourW[,18]);lines(1:62, sORP49HourW[,18], type="l", col="red")
 plot(sORP49HourW[,36]);lines(1:62, sORP49HourW[,36], type="l", col="red")


plot(sCON49HourW[,1]);lines(1:62, sCON49HourW[,1], type="l", col="red")
plot(sCON49HourW[,18]);lines(1:62, sCON49HourW[,18], type="l", col="red")
 plot(sCON49HourW[,36]);lines(1:62, sCON49HourW[,36], type="l", col="red")
 
 plot(sPH49HourW[,1]);lines(1:61, sPH49HourW[,1], type="l", col="red")
 plot(sPH49HourW[,18]);lines(1:61, sPH49HourW[,18], type="l", col="red")
 plot(sPH49HourW[,36]);lines(1:61, sPH49HourW[,36], type="l", col="red")



plot(sORP20HourW[,1]);lines(1:62, sORP20HourW[,1], type="l", col="red", main= "S20")
 plot(sORP20HourW[,18]);lines(1:62, sORP20HourW[,18], type="l", col="red")
 plot(sORP20HourW[,36]);lines(1:62, sORP20HourW[,36], type="l", col="red")


plot(sCON20HourW[,1]);lines(1:62, sCON20HourW[,1], type="l", col="red")
plot(sCON20HourW[,18]);lines(1:62, sCON20HourW[,18], type="l", col="red")
 plot(sCON20HourW[,36]);lines(1:62, sCON20HourW[,36], type="l", col="red")
 
 plot(sPH20HourW[,1]);lines(1:61, sPH20HourW[,1], type="l", col="red")
 plot(sPH20HourW[,18]);lines(1:61, sPH20HourW[,18], type="l", col="red")
 plot(sPH20HourW[,36]);lines(1:61, sPH20HourW[,36], type="l", col="red")

plot(sORP36HourW[,1]);lines(1:62, sORP36HourW[,1], type="l", col="red", main= "S36")
 plot(sORP36HourW[,18]);lines(1:62, sORP36HourW[,18], type="l", col="red")
 plot(sORP36HourW[,36]);lines(1:62, sORP36HourW[,36], type="l", col="red")

plot(sCON36HourW[,1]);lines(1:62, sCON36HourW[,1], type="l", col="red")
plot(sCON36HourW[,18]);lines(1:62, sCON36HourW[,18], type="l", col="red")
 plot(sCON36HourW[,36]);lines(1:62, sCON36HourW[,36], type="l", col="red")
 
 plot(sPH36HourW[,1]);lines(1:61, sPH36HourW[,1], type="l", col="red")
 plot(sPH36HourW[,18]);lines(1:61, sPH36HourW[,18], type="l", col="red")
 plot(sPH36HourW[,36]);lines(1:61, sPH36HourW[,36], type="l", col="red")



```


```{r}
#Combine plot CON

plot(range(1:62), range(c(sCON25HourW[,1],sCON25HourW[,18], sCON25HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON25HourW[,1], col="red")
lines(1:62, sCON25HourW[,18], col="blue")
lines(1:62, sCON25HourW[,36], col="green")




plot(range(1:62), range(c(sCON29HourW[,1],sCON29HourW[,18], sCON29HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON29HourW[,1], col="red")
lines(1:62, sCON29HourW[,18], col="blue")
lines(1:62, sCON29HourW[,36], col="green")



plot(range(1:62), range(c(sCON30HourW[,1],sCON30HourW[,18], sCON30HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON30HourW[,1], col="red")
lines(1:62, sCON30HourW[,18], col="blue")
lines(1:62, sCON30HourW[,36], col="green")





plot(range(1:62), range(c(sCON27HourW[,1],sCON27HourW[,18], sCON27HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON27HourW[,1], col="red")
lines(1:62, sCON27HourW[,18], col="blue")
lines(1:62, sCON27HourW[,36], col="green")



# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:62), range(c(sCON35HourW[,1],sCON35HourW[,18], sCON35HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON35HourW[,1], col="red")
lines(1:62, sCON35HourW[,18], col="blue")
lines(1:62, sCON35HourW[,36], col="green")



plot(range(1:62), range(c(sCON43HourW[,1],sCON43HourW[,18], sCON43HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON43HourW[,1], col="red")
lines(1:62, sCON43HourW[,18], col="blue")
lines(1:62, sCON43HourW[,36], col="green")



plot(range(1:62), range(c(sCON33HourW[,1],sCON33HourW[,18], sCON33HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON33HourW[,1], col="red")
lines(1:62, sCON33HourW[,18], col="blue")
lines(1:62, sCON33HourW[,36], col="green")



plot(range(1:62), range(c(sCON11HourW[,1],sCON11HourW[,18], sCON11HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON11HourW[,1], col="red")
lines(1:62, sCON11HourW[,18], col="blue")
lines(1:62, sCON11HourW[,36], col="green")



plot(range(1:62), range(c(sCON22HourW[,1],sCON22HourW[,18], sCON22HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON22HourW[,1], col="red")
lines(1:62, sCON22HourW[,18], col="blue")
lines(1:62, sCON22HourW[,36], col="green")

# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:62), range(c(sCON17HourW[,1],sCON17HourW[,18], sCON17HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON17HourW[,1], col="red")
lines(1:62, sCON17HourW[,18], col="blue")
lines(1:62, sCON17HourW[,36], col="green")



plot(range(1:62), range(c(sCON31HourW[,1],sCON31HourW[,18], sCON31HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON31HourW[,1], col="red")
lines(1:62, sCON31HourW[,18], col="blue")
lines(1:62, sCON31HourW[,36], col="green")




plot(range(1:62), range(c(sCON26HourW[,1],sCON26HourW[,18], sCON26HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON26HourW[,1], col="red")
lines(1:62, sCON26HourW[,18], col="blue")
lines(1:62, sCON26HourW[,36], col="green")



plot(range(1:62), range(c(sCON14HourW[,1],sCON14HourW[,18], sCON14HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON14HourW[,1], col="red")
lines(1:62, sCON14HourW[,18], col="blue")
lines(1:62, sCON14HourW[,36], col="green")



plot(range(1:62), range(c(sCON19HourW[,1],sCON19HourW[,18], sCON19HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON19HourW[,1], col="red")
lines(1:62, sCON19HourW[,18], col="blue")
lines(1:62, sCON19HourW[,36], col="green")


# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:62), range(c(sCON12HourW[,1],sCON12HourW[,18], sCON12HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON12HourW[,1], col="red")
lines(1:62, sCON12HourW[,18], col="blue")
lines(1:62, sCON12HourW[,36], col="green")



plot(range(1:62), range(c(sCON49HourW[,1],sCON49HourW[,18], sCON49HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON49HourW[,1], col="red")
lines(1:62, sCON49HourW[,18], col="blue")
lines(1:62, sCON49HourW[,36], col="green")



plot(range(1:62), range(c(sCON20HourW[,1],sCON20HourW[,18], sCON20HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON20HourW[,1], col="red")
lines(1:62, sCON20HourW[,18], col="blue")
lines(1:62, sCON20HourW[,36], col="green")



plot(range(1:62), range(c(sCON36HourW[,1],sCON36HourW[,18], sCON36HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sCON36HourW[,1], col="red")
lines(1:62, sCON36HourW[,18], col="blue")
lines(1:62, sCON36HourW[,36], col="green")




```
## Compned plot ORP
```{r}
plot(range(1:62), range(c(sORP25HourW[,1],sORP25HourW[,18], sORP25HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP25HourW[,1], col="red")
lines(1:62, sORP25HourW[,18], col="blue")
lines(1:62, sORP25HourW[,36], col="green")


plot(range(1:62), range(c(sORP29HourW[,1],sORP29HourW[,18], sORP29HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP29HourW[,1], col="red")
lines(1:62, sORP29HourW[,18], col="blue")
lines(1:62, sORP29HourW[,36], col="green")



plot(range(1:62), range(c(sORP30HourW[,1],sORP30HourW[,18], sORP30HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP30HourW[,1], col="red")
lines(1:62, sORP30HourW[,18], col="blue")
lines(1:62, sORP30HourW[,36], col="green")





plot(range(1:62), range(c(sORP27HourW[,1],sORP27HourW[,18], sORP27HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP27HourW[,1], col="red")
lines(1:62, sORP27HourW[,18], col="blue")
lines(1:62, sORP27HourW[,36], col="green")



# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:62), range(c(sORP35HourW[,1],sORP35HourW[,18], sORP35HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP35HourW[,1], col="red")
lines(1:62, sORP35HourW[,18], col="blue")
lines(1:62, sORP35HourW[,36], col="green")



plot(range(1:62), range(c(sORP43HourW[,1],sORP43HourW[,18], sORP43HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP43HourW[,1], col="red")
lines(1:62, sORP43HourW[,18], col="blue")
lines(1:62, sORP43HourW[,36], col="green")



plot(range(1:62), range(c(sORP33HourW[,1],sORP33HourW[,18], sORP33HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP33HourW[,1], col="red")
lines(1:62, sORP33HourW[,18], col="blue")
lines(1:62, sORP33HourW[,36], col="green")



plot(range(1:62), range(c(sORP11HourW[,1],sORP11HourW[,18], sORP11HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP11HourW[,1], col="red")
lines(1:62, sORP11HourW[,18], col="blue")
lines(1:62, sORP11HourW[,36], col="green")



plot(range(1:62), range(c(sORP22HourW[,1],sORP22HourW[,18], sORP22HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP22HourW[,1], col="red")
lines(1:62, sORP22HourW[,18], col="blue")
lines(1:62, sORP22HourW[,36], col="green")

# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:62), range(c(sORP17HourW[,1],sORP17HourW[,18], sORP17HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP17HourW[,1], col="red")
lines(1:62, sORP17HourW[,18], col="blue")
lines(1:62, sORP17HourW[,36], col="green")



plot(range(1:62), range(c(sORP31HourW[,1],sORP31HourW[,18], sORP31HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP31HourW[,1], col="red")
lines(1:62, sORP31HourW[,18], col="blue")
lines(1:62, sORP31HourW[,36], col="green")



plot(range(1:62), range(c(sORP26HourW[,1],sORP26HourW[,18], sORP26HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP26HourW[,1], col="red")
lines(1:62, sORP26HourW[,18], col="blue")
lines(1:62, sORP26HourW[,36], col="green")



plot(range(1:62), range(c(sORP14HourW[,1],sORP14HourW[,18], sORP14HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP14HourW[,1], col="red")
lines(1:62, sORP14HourW[,18], col="blue")
lines(1:62, sORP14HourW[,36], col="green")



plot(range(1:62), range(c(sORP19HourW[,1],sORP19HourW[,18], sORP19HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP19HourW[,1], col="red")
lines(1:62, sORP19HourW[,18], col="blue")
lines(1:62, sORP19HourW[,36], col="green")


# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:62), range(c(sORP12HourW[,1],sORP12HourW[,18], sORP12HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP12HourW[,1], col="red")
lines(1:62, sORP12HourW[,18], col="blue")
lines(1:62, sORP12HourW[,36], col="green")



plot(range(1:62), range(c(sORP49HourW[,1],sORP49HourW[,18], sORP49HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP49HourW[,1], col="red")
lines(1:62, sORP49HourW[,18], col="blue")
lines(1:62, sORP49HourW[,36], col="green")



plot(range(1:62), range(c(sORP20HourW[,1],sORP20HourW[,18], sORP20HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP20HourW[,1], col="red")
lines(1:62, sORP20HourW[,18], col="blue")
lines(1:62, sORP20HourW[,36], col="green")



plot(range(1:62), range(c(sORP36HourW[,1],sORP36HourW[,18], sORP36HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:62, sORP36HourW[,1], col="red")
lines(1:62, sORP36HourW[,18], col="blue")
lines(1:62, sORP36HourW[,36], col="green")


```
# Combined plot PH
```{r}

plot(range(1:61), range(c(sPH25HourW[,1],sPH25HourW[,18], sPH25HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH25HourW[,1], col="red")
lines(1:61, sPH25HourW[,18], col="blue")
lines(1:61, sPH25HourW[,36], col="green")


plot(range(1:61), range(c(sPH29HourW[,1],sPH29HourW[,18], sPH29HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH29HourW[,1], col="red")
lines(1:61, sPH29HourW[,18], col="blue")
lines(1:61, sPH29HourW[,36], col="green")



plot(range(1:61), range(c(sPH30HourW[,1],sPH30HourW[,18], sPH30HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH30HourW[,1], col="red")
lines(1:61, sPH30HourW[,18], col="blue")
lines(1:61, sPH30HourW[,36], col="green")





plot(range(1:61), range(c(sPH27HourW[,1],sPH27HourW[,18], sPH27HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH27HourW[,1], col="red")
lines(1:61, sPH27HourW[,18], col="blue")
lines(1:61, sPH27HourW[,36], col="green")



# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:61), range(c(sPH35HourW[,1],sPH35HourW[,18], sPH35HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH35HourW[,1], col="red")
lines(1:61, sPH35HourW[,18], col="blue")
lines(1:61, sPH35HourW[,36], col="green")



plot(range(1:61), range(c(sPH43HourW[,1],sPH43HourW[,18], sPH43HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH43HourW[,1], col="red")
lines(1:61, sPH43HourW[,18], col="blue")
lines(1:61, sPH43HourW[,36], col="green")



plot(range(1:61), range(c(sPH33HourW[,1],sPH33HourW[,18], sPH33HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH33HourW[,1], col="red")
lines(1:61, sPH33HourW[,18], col="blue")
lines(1:61, sPH33HourW[,36], col="green")



plot(range(1:61), range(c(sPH11HourW[,1],sPH11HourW[,18], sPH11HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH11HourW[,1], col="red")
lines(1:61, sPH11HourW[,18], col="blue")
lines(1:61, sPH11HourW[,36], col="green")



plot(range(1:61), range(c(sPH22HourW[,1],sPH22HourW[,18], sPH22HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH22HourW[,1], col="red")
lines(1:61, sPH22HourW[,18], col="blue")
lines(1:61, sPH22HourW[,36], col="green")

# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:61), range(c(sPH17HourW[,1],sPH17HourW[,18], sPH17HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH17HourW[,1], col="red")
lines(1:61, sPH17HourW[,18], col="blue")
lines(1:61, sPH17HourW[,36], col="green")



plot(range(1:61), range(c(sPH31HourW[,1],sPH31HourW[,18], sPH31HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH31HourW[,1], col="red")
lines(1:61, sPH31HourW[,18], col="blue")
lines(1:61, sPH31HourW[,36], col="green")




plot(range(1:61), range(c(sPH26HourW[,1],sPH26HourW[,18], sPH26HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH26HourW[,1], col="red")
lines(1:61, sPH26HourW[,18], col="blue")
lines(1:61, sPH26HourW[,36], col="green")



plot(range(1:61), range(c(sPH14HourW[,1],sPH14HourW[,18], sPH14HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH14HourW[,1], col="red")
lines(1:61, sPH14HourW[,18], col="blue")
lines(1:61, sPH14HourW[,36], col="green")



plot(range(1:61), range(c(sPH19HourW[,1],sPH19HourW[,18], sPH19HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH19HourW[,1], col="red")
lines(1:61, sPH19HourW[,18], col="blue")
lines(1:61, sPH19HourW[,36], col="green")


# sPH25, sPH29, sPH30, sPH27, sPH35, sPH43, sPH33, sPH11, sPH22, sPH17, sPH31, sPH26, sPH14, sPH19,  sPH12, sPH49, sPH20, sPH36

plot(range(1:61), range(c(sPH12HourW[,1],sPH12HourW[,18], sPH12HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH12HourW[,1], col="red")
lines(1:61, sPH12HourW[,18], col="blue")
lines(1:61, sPH12HourW[,36], col="green")



plot(range(1:61), range(c(sPH49HourW[,1],sPH49HourW[,18], sPH49HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH49HourW[,1], col="red")
lines(1:61, sPH49HourW[,18], col="blue")
lines(1:61, sPH49HourW[,36], col="green")



plot(range(1:61), range(c(sPH20HourW[,1],sPH20HourW[,18], sPH20HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH20HourW[,1], col="red")
lines(1:61, sPH20HourW[,18], col="blue")
lines(1:61, sPH20HourW[,36], col="green")



plot(range(1:61), range(c(sPH36HourW[,1],sPH36HourW[,18], sPH36HourW[,36]), na.rm=TRUE), type='n')
legend("topright", lty=c(1,1), col=c("red","blue", "green"), legend=c("1", "18", "36"))

lines(1:61, sPH36HourW[,1], col="red")
lines(1:61, sPH36HourW[,18], col="blue")
lines(1:61, sPH36HourW[,36], col="green")



```



